
\subsection{Sizes}\label{subsec:sizes}

\begin{tabular}{r|ll}
    Sectors & Mechclass & Weight\\
    0 &Human & 0.1\\
    1 &Exo& 0.6\\
    2 &Exo,Tiny& 1\\
    3 &Tiny & 2\\
    4 &Tiny, Very Light & 4\\
    5 &Very Light& 10\\
    6 &Very Light, Light& 18\\
    7 &Light& 40\\
    8 &Light, Medium& 70\\
    9 &Medium& 150\\
    10 &Medium, Heavy& 300\\
    11 &Heavy& 500\\
    12 &Heavy, Very Heavy& 700\\
    13 &Very Heavy& 900\\
    14 &Very Heavy& 1200\\
    15 &Very Heavy, Ultra& 1500\\
    16+ &Ultra& >1500t\\
\end{tabular}\par
Modules are assigned to sectors.
Each sector has a size of 1, a module takes up some of that size.
Modules can be spread over multiple Sectors, as long as they are adjacent, although this will increase the likelyhood
of it sustaining damage.
Some Modules require a Hardpoint, there is generally only one Hardpoint per Sector.\par
A Mech has an effective Tech Level of the Tech at the 90\% point of the sizes modules ordered by Tech Level.\par
Contamination Damage applies to the highest Tech modules first.
Each Module can be damaged individually.\par

\input{mecha/systems}

\section{Misc Modules}\label{sec:miscmodules}
\par
\subsection{Basetech}\label{subsec:basetech}
\subsubsection{Water Distillery}\label{subsubsec:water-distillery}
Energy Cost: 50kw\par
Heat: 10\par
Weight: 0.5t\par
Turns 1L of Dirty Water into 1L of Contaminated Water per minute\par
Requires Reprocessing\par
\par

\subsubsection{Cargo compartment}\label{subsubsec:cargo-compartment}
stores up to 1 t of Cargo\par
Weight: 0.5t for Size Calculation, Empty weight 0.1t, Full 1.1t for speed calculation (if relevantt)
\par
\section{Lowtech}\label{sec:lowtech}
\subsubsection{Basic Food Processor}
Energy Cost per operation: 10kw \par
Heat: 5 \par
Size:0.5t\par
Detoxes and prepares up to 5kg of Food in 30 minutes \par
Requires Reprocessing\par

\subsubsection{Basic Air Filter}
Energy Cost per operation: 15kw \par
Heat: 2\par
Size:0.5\par
Decontaminates and pressurizes 3000 L of air in  10 minutes or double without pressurizing. \par
Requires Decon 1\par
Airtank 10 Liter @ 300 bar contains 3000L of air.
Air is used at 10 Liters/Minute so a 10 Liter air tank lasts about 5 hours of calm
walking or half (or even less) when doing strenuous activity.
1.225 kg/m3: 3.675 Kg of air
+ 15kg for Tank, Valve und Hose
\par
\subsubsection{Basic Decon Equipment}
Energy Cost per operation: 20 kw \par
Clean Water Cost 10:1\par
Heat: 10 \par
Size: 0.5\par
Allows to lower Objects contamination by washing them, if applicable.
Rate requires 1 hour per Kilogram, Contamination is 1/10 of starting value.
Used water is Contaminated\par

Optical Sensors\par
Energy: 1\par
Size: 0.25 \par
Rating: 100\par
Provides Targetting Lock is obtained\par
Visual Lock: Distance/Rating <= Target Size (+Camouflage and visual impairments)\par

Thermal Sensors\par
Energy: 1\par
Size 0.25\par
Rating 100\par
Thermal Lock: Distance/Rating <= Target Thermal Signature\par

\subsubsection{Basic Computer System}\par
Weight 500kg\par
Energy: 0.1\par
Module: Processor or Memory\par
\par
\section{Midtech}\label{sec:midtech}
\subsubsection{ComputerSystem}:
Weight 100 kg
Energy: 0.1
Module: Processor or Memory\par

Nondeterministic Computation Core:\par
Size 0.5\par
Energy: 0.5\par
Module: Processor\par
Requires Black Biotech 3\par

Extended Decon Equipment\par
Energy Cost per Operation: 36k (10/s)\par
Alacast Cost per Operation: 5g\par
Size: 1
Allows to turn Contaminated Objects into uncontaminated Objects at the rate of 100kg/h if suitable\par
If used on Humans, Roll Red Biotech, on 9 or more, removes one Charactertaint.\par
Always Inflicts Wound of Level 11-RollResult\par
Requires Decon 3\par

Extended Detox Equipment:\par
Energy Cost per Operation: 36k (10/s)\par
Size 0.75\par
Allows Detoxing and Preparing of up to 1t/h\par
If used on Humans, Roll Red Biotech, on 6 or more, remove all Infections and appropriate Toxins.\par
Always Inflicts Wound of Level 8-RollResult\par
Requires Detox 3\par
Automedic:
Energy Cost: 6k(variable - 10/s for 10 min)\par
Size: 0.75\par
Supplies tools of Medic/ supplies good operating conditions for Medic / reduces the use of Medicine by half / allows stasis\par
Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
double Advantage or autonomously attempts the procedure at Level 3 mod -1.\par
If not, Instead supplies one Advantage.\par
Software may supply the Red Biotech roll even autonomously.\par
Stasis is automatic and slows down the daily/hourly tickrate (including Healing and Contamination) by a factor of 10
(additive) for every energy point per second.
This is a medical coma, not timedilation.
\section{Hightech}\label{sec:hightech}
Advanced Detox-Decon Equipment \par
Size: 1\par
Energy Cost per Operation 72k (variable 20/s for 1 h)\par
Alacast Usage per Operation if Detainting: 1g/t of raw material, 10g/human\par
Detoxes and Detaints up to 5t of material, including air and water.\par
Living Entities suffer no harm, and on a 4 or more on a Red Biotech Roll lose one Taint level.
Furthermore all Infections and Appropriate Toxins are removed.\par
Requires Detox 4 and Decon 4

Advanced AutoMedic\par
Energy Cost: 3k (variable - 5/s for 10 min)\par
size: 1

Allows Medic Rolls/ supplies very good operating conditions for Medic Rolls/ reduces the use of Medicine by 90\%/allows Ressurection\par
To Treat a wound:\par
Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
triple Advantage or autonomously attempts the procedure at Level 4 mod -1.\par
If not, Instead supplies one Advantage or autonomously attempts the procedure at Level 2.\par
Software may supply the Red Biotech roll even autonomously.\par
To Ressurect:\par
requires 1g of EOL per total spent points on a character (or 20* the average level of an NPC)
Roll Black Biotech, every 15\% missing from the corpse or order of magnitude in days that has passed since the time of death
lowers the final score by 1.
If the roll succeeds, place 5 wounds of severity 15-result on that character, they lose
one level from the highest Ability and one from the highest Skill and are alive again.
If the roll does not succeed,
5\% of the total corpse and the dosage of EOL is lost.

