\section{Systems}\label{sec:systems}
A Mech needs a movement system, energy and heat systems and should probably have a seal, weapons and support systems.
\subsection{Costs}\label{subsec:costs}
Systems Examples\par
\begin{tabular}{c|c|l}
    Tech    & Credits Cost    & Examples\\
    B    &    4        &    \makecell*[{{p{12cm}}}]{Water Destillery, Rail based movement system, simple wheels,
    Manned gun, Ramshield, Floatation,   Metal Armorplating , Extra Cargo (10), steam engine, passive cooling}\\&&\\
    L    &    5        &    \makecell*[{{p{12cm}}}]{Lowtech Detox-Decon Equip(LDDE; +1), suspended wheels, tracks,
    bipedal, Dynamo , Autoturret, Jumpjets, Mech sized Sword, water cooling circle, basicHeatsink }\\&&\\
    M    &    6        &    \makecell*[{{p{12cm}}}]{Shields, flexible/balanced bipedal, Boostjets,
    Deployable Solar Panel, Sensorarray,  MDDE (+2), Base AI system, Mech sized Weaponry (Advanced
    (Vibro/electro/Monofilament) Sword), Rocketlauncher, Water venting system, midtech Heatsink}\\&&\\
    H    &    7        &    \makecell*[{{p{12cm}}}]{BCI, Advanced AI, WeaponLaser, Sustained Flight,  Advanced
    Shields, Nano Repair Cloud, Automedic, OVERDRIVE mode, Hightech Heatsink}\\&&\\
    E    &    8        &    \makecell*[{{p{12cm}}}]{Quantum Lookahead Sensors, Blink Teleporter, Timerift Shields
    (Delays Damage 1d10 rounds), EnergySword}
\end{tabular}\par
Designtarget (TODO: write words good) for normal fighting mech

\begin{enumerate}[label = - ]
\item 20\% movement
\item 20\% weaponry
\item 5\% energy
\item 5\% Cargo
\item 50\% + armor
\end{enumerate}


\subsection{Energy Systems}\label{subsec:energy-systems}
Energy Systems usually do not use a hardpoint.

\textbf{Power to Weight} is how much maximum output power per weight the system provides.

\textbf{Input} of an Energy System is generally considered its "fuel", but can also just be batteries or similar.
The Input is stored with other Cargo.

\textbf{Efficiency} is the function with input x being ratio of poweroutput vs maximum power output and result of
efficiency.
In parenthesis at the end is the efficiency at 100\%

\textbf{Output} is set during addition/modification of the system
(Engineering:Repair+ system specific skill, Competence vs 8, 4h).
By Default there are only 2 Modes: Power saving and Full Throttle.
Mode usage is marked for full hours spent in them, with the higher usage overriding the lower usage, except when the
remaining Energy is less than an hour, where minute/round calculations might be needed.
Energy E is in Rates of kilojoules/round, since Rounds are 5 seconds long, 1 Energy is equivalent to 5kw over 1 Round.
1 MJ is 1000 kJ so 1 MJ = 200E

\begin{tabular}{l|cccl}
    Type & E per t & heat/r per t & input & efficiency\\
    \hline Basetech \\
    Steampower & 0.7 & 8 & Coal & 10\%\\
    FlyWheel & 20 & 0 & stored & loses 10\% per turn \\
    Crew & 0.01 & 0 & Labor & 10\%\\
    \hline Lowtech \\
    Combustion Motor& 140 & 2  & Combustible & 40\% \\
    \hline Midtech \\
    PEM & 100 & 0.1 & Hydrogen & 90\%\\
    Solar Panel & 10 & 2 & Sunlight & Contamination dependent\\
    Batteries & 10 & 2 & stored & loses 10\% per month \\
    \hline Hightech \\
    Reactor & 300 & 5  & Fuelrods & 8\%\\
    CFReactor & 40 & 0.1  & Deuterium & 80\%\\
    Capacitor & 1000 & X & stored & loses 10\% per hour
\end{tabular}


\textbf {Solar Panel} Deploying takes 5 turns times 100w or 5 minutes labor, any damage received while deployed
will also damage the Solar panel, production halved every 5 contamination levels, only works during day

\textbf {CFReactor} Cold Fusion requires start up energy, equaling the Output for 1 Round.

\textbf {Deuterium} 1 kg - 4.5 TJ or 900,000,000E (effective at 80\%= 720ME)

\textbf {Fuel Rod} 1 kg - 75 TJ or 15,000,000,000E (effective at 8\%= 120ME)

\textbf {Hydrogen} 70kg (1000L) = 10,082MJ or 2,016,400E (effective at 90\% = 1,814,760E)

\textbf {HFC-10} 10 liter - hydrogen fuel cell: Cylinder 20cm diameter,
35 cm height or 23cm cube=10L. \par
containing 9 MJ or 1800E

\textbf {HFC-50} 50 liter - hydrogen fuel cell: Cylinder 40cm diameter,
40 cm height or 37cm cube = 50L,
\par containing 45 MJ or 9000E\par
contains low power sub system used to power up basic systems (like hydrogen gas pumps for the PEM Stacks)

\textbf{CombustionFuel} 800kg (1000L) = 40,000MJ or 8,000,000E (3,2ME)

\textbf{Battery} has 180kE/ t

\textbf{Capacitor} generates 1 Heat per 10 Energy moved, for all other purposes instant

\subsection{Movement Systems}\label{subsec:movementsystems}

\textbf{Efficiency} is the ratio of power consumed to power used to move the mech

\textbf{Drag} is the general amount of power wasted the faster the mech is going

\textbf{Power to Weight} is how much maximum movement power the system can employ per weight

\begin{tabular}{l|ccccccl}
    Type    & Energy/r & \makecell[l]{GroundCoefficient\\ per ton} & Area per sector & Power per ton & hardpoints &Extra\\
    \hline Basetech\\
    Rail                 & 55 & 0.001 & 20 & 500 & 50\% & rails \\
    Simple Wheels        & 100 & 8 & 1 & 750 & 25\% & flat terrain \\
    Floatation           & 15 & 2 & 1000 & 90 & 10\% & water\\
    \hline Lowtech\\
    Complex Wheels       & 175 & 6 & 3 & 1500 & 25\% &  somewhatflat terrain \\
    Tracks               & 100 & 0.02 & 40 & 600 & 33\% & rough terrain\\
    2 Simple Legs        & 30 & 0.5 & 100 & 450 & 25\% & all terrain\\
    4 Simple Legs        & 30 & 0.2 & 200 & 450 & 25\% & all terrain\\
    6 Simple Legs        & 30 & 0.13 & 300 & 450 & 25\% & all terrain\\
    Jumpjets             & 1000 & 50 & 1 & 1000 & 1 & upwards\\
    \hline Midtech\\
    2 Flexible Legs      & 100 & 10 & 10 & 1000 & 30\% &  like a large human\\
    4 Flexible Legs      & 100 & 1 & 100 & 1000 & 30\% &  like a large human\\
    6 Flexible Legs      & 100 & 0.3 & 1000 & 1000 & 30\% &  like a large human\\
    Boostjets            & 2000 & 5 & 0.1 & 1000 & 2 &  any direction\\
    \hline Hightech\\
    Spiderwalker         & 150 & 0.1 & 500 & 400 & 50\% & any surface
\end{tabular}

Accelleration is assumed to be able to change to 50\%/80\%/100\% of max speed  in the first/second/third round\par
Pneumatic variants of the legs weigh half as much but are constrained to weightclasses light and below\par

\subsubsection{Maximum Speed}
Since Power is in Watt, aka
\(\frac{kg*m*m}{s*s*s}\)
``all'' that is needed to get the max speed in
\(\frac{m}{s}\) is to get
the friction forces at the point of highest velocity in \(\frac{kg*m}{s*s}\), aka Newton.
The GroundCoefficient is the one given in the Table, Power has to be calculated
\(Friction = Mass* GroundCoefficient/100 * 9.81\)\par
Repeat updating Airdrag\par
\(Airdrag = \frac{Airdrag + 0.5*Area*1.225 * Speed^2}{2}\)
and Speed\par
\(Speed = \frac{Power}{Airdrag + Friction}\)\par
Until the maximum value is found.\par
Bonus Formulae:\par
\(Airdrag = \frac(49*Speed^2*Area)/80 \) \par
\(Speed = \frac{Power}{(49*Speed^2*Area)/80 + Friction}\)


\subsection{Heat Systems}\label{subsec:heat-systems}
Warning: ALL Dissipated heat contributes to IR signature
\textbf{Input} is the amount of power the Heat System requires to function actively
\textbf{Weight} direct weight of the system
\textbf{Cooling} how much heat is dissipated, passively/actively.
\textbf{Capacity} how much heat can be stored in this system.
Cumulative for the mech.

\begin{tabular}{r|lllll}
    Type & Input & Cooling & Capacity & Hardpoints\\
    \hline Basetech\\
    Small Heatsink & 0 & 0.4 & 30 & \\
    \hline Lowtech\\
    Radiator Vent & 2 E/r & p+t;2p+5t & 0 & 1+\\
    Large Heatsink & 0 & 0.5 & 50 & \\
    \hline Midtech\\
    Optimized heatsink  & 0 & 1 & 40 & \\
    Coolant Dump  & 50 E & 0;25 & 25 & 1 \\
    Radiator Wings & 0.1 E/r & 0;10\% & 50 & 1\\
    \hline Hightech\\
    Fractal heatsink & 10 E/r & 1.5/0 & 100 & \\
    OVERDRIVE & 1000E & 0 &  0 &
\end{tabular}

\textbf{Heatsinks}: store Heat and slowly release it.

\textbf{Radiator Vent}: Use at least one Hardpoint for the vent.
Cooling scales with Hardpoints(p) and Tonnage(t)

\textbf{Coolant Dump}: Uses a Hardpoint for any number of CoolantDumps When triggered using 50E total,
releases 25 stored heat together with 25L water, as a thermal barrier.
Uses is Decoys and Intuition.


\textbf{Radiator Wings}: Deploying takes 5 turns and 1E or 5 minutes labor, any damage received while deployed
will also damage the Radiator Wings: radiates 10\% of total system heat, as long as 0.2E/r (for coolant pumping)
is applied.

\textbf{Overdrive}: When triggered, enter Overdrive Mode: Energy and Movement Systems count double (except for weight),
Heat is spent insteadof gained.
When heat drops to 0 or below, Mech shuts down for 20 rounds, reduced by a Gadgets+Piloting,Intuition roll and
Overdrive requires a Competence, Gadgets-Repair;
10m;
Threshhold of 10 to repair.

\subsection{Sealsystems}\label{subsec:sealsystems}
\textbf{Level} how much the seal reduces Contamination behind it.
\textbf{Resistance} how much damage it takes to damage the Seal.
For each Instance of Damage at or above the Resistance, it's Resistance is lowered by 1.

\begin{tabular}{l|r|r|r}
    Tech & Seal Level & Resistance & Cost/Sector\\\hline
    Base &  6 & 2 & 1\\
    Low &   13& 3 & 2\\
    Mid &   21& 4 & 3\\
    High &  30& 5 & 4\\
    Experimental& 50 & 2 &8
\end{tabular}\par

\subsection{Weapons}\label{subsec:weapons}
\textbf{Damage}
\textbf{Threshholds}
\textbf{Costs}
\textbf{Skills}

Melee weapons rely on the movement System, so their costs are in meters that are used to attack rather than move\par
\begin{tabular}{c|clll}
    Type & Damage & Threshholds & Costs & Weight\\
    \hline \hline BaseTech&&&&\\
    \hline
    Metal Sword & 10 & 10m[5,7,9,11,13,15,17,19,20]0 & 30m & 5t \\
    \hline
    Manned Turret & X & X & \makecell[l]{manual \\labor +X} &  X +50\% \\
    \hline \hline Lowtech &&&&\\
    \hline
    Heavy Machinegun & 30 & \makecell[l]{100m[3,6,10,14,18]20\\
                                        500m[5, 8, 12,15]10\\
                                        1000m[7,10,14]5\\
                                        2km[11,16]5\\
                                        8km[15]1 indirect}& 5kg, 5H & 100kg \\
    \hline
    Light Artillery & 120 & \makecell[l]{7km[8,12,16,20]1 \\
                                        15km[10,14]}& 50kg, 10H & 8t  \\
    \hline
    120mm Smoothbore & 120 & \makecell[l]{50m[10,20]3\\
                                        100m[6,10,14]8\\
                                        500m[5,7,9,11]15\\
                                        2km[8,10,12,14,16]20\\
                                        4km[11,13,15,20]10 indirect\\
                                        8km[13,17]5 indirect}
                                            & 20kg 5H & 20t \\
    \hline\hline Midtech &&&&\\
    \hline
    Autocannon & 80 & \makecell[l]{10m[10]3\\
                                  200m[5,8,11,14,17,20]15\\
                                  1km[8,12,16,20]20\\
                                  2km[10,14,18]10 \\
                                  4km[13,17,20]5 indirect }
                                        & 7kg 5H & 5t \\
    \hline
    Pulse Laser & 60 & \makecell[l]{1km[5,-15]50\\
                                   5km[7,9,11,13,15]100\\
                                   LOS[10,12,14,16,18]100}
                                        & 1000E 10H & 7t\\
    \hline
    Precision Cannon & 140 & \makecell[l]{500m[7,10,13]2\\
                                         2km[7-11,13,15,17,19]30\\
                                         LOS[8,10,12,14,16,18,20]25}
                                        & 15 kg 10H & 10t\\
    \hline
    Rocket Launcher x 8 & X & X & X & 500kg \\
    \hline\hline Hightech &&&&\\
    \hline
    Rocket Platform & X & X & X & 1500 kg \\
    \hline
    Railgun & 160 & \makecell[l]{200m[7,9,11,13,15]5\\
                                1km[5,7,9,11,13]10\\
                                4km[7,9,11,13,15]5\\
                                12km[9,11,13,15,17]1}
                                & 50 kg, 25H, 4000E & 15t\\
    \hline
    Advanced Pulse Laser & 90 & \makecell[l]{3km[5-20]50\\
                                   9km[7,9,11,13,15,17]100\\
                                   LOS[10,12,14,16,18]100}
                                        & 1800E 15H & 3t\\
    \hline
    Ramping Beam Laser & 10\(\times\)X & \makecell[l]{1km[5,10,15]10\\
                                          LOS[10,15]100}
                        & X\(\times\)(10E 1H) & 10t\\

\end{tabular}\par

\textbf{Notes}:
\begin{enumerate}[label = - ]
\item Melee Weapons: Ignore Shields
\item Manned Turret: X Depends on the mounted gun and the skill of the gunner
\item Light Artillery: Attacks take 1s per 300m distance, rounded up, minimum range 100m
\item 120mm Smoothbore: Can only fire every second round, requires Indirect for targets further away than 2k
\item Autocannon: may make another attack instantly for double the cost
\item Basic Pulse Laser: -0.1*contamination level dmg per km, rounded mathematically
\item Precision Cannon: Needs to be stationary to aim and fire, 1 turn of aiming between shots
\item Rocket Launcher: Ignores Shields
\item Rocket Platform: Ignores Shields, Beam rules
\item Railgun: Needs to be stationary to fire.
Loading takes 2 turns.
\item Advanced Pulse Laser: -0.1*contamination level dmg per km, rounded mathematically
\item Ramping Beam Laser: Every round, X increases by 1 while shooting, decreases by 1 down to 0 otherwise.
\end{enumerate}


\subsection{Defensesystems}\label{subsec:defensesystems}
Defensesystems are configured using the relevant \hyperref[subsubsec:defense]{Technical Skill},
the relevant usage Method, usually \hyperref[subsec:computer]{Computer Usage}
with (if not explicitly defined) the threshholds [5,8,13,16,19] or automatically by a Program of the corresponding level.


Configuration, Strength are the  armor-equivalent statistics a shield provides.
Configuration is required to start a Shield and takes 1 Action, if the lowest threshhold is not hit, the Configuration
is 0, but the Shield still starts.

Coldboot can only be done after all Systems have been shut off for at least one turn.

Shields turn off when overwhelmed and have to meet the Reboot requirements (including another Configuration) to turn
back on.
Config X means that the specific Configuration Threshhold of X has to be reached.
Each Sector requires a Defensesystem on its own.
Defensesystems provide coverage for the Sector that they are in first, but if multiple levels (representing a larger
Generator) are present they can (during configuration) be spread to adjacent Sectors.
Deflectors and Dampeners provide their effects, if they do not cover all sectors, by rounding the portion of sectors
that are uncovered up to the nearest tenth and rolling a single die (Fate point adds Fate Bonusdice).
If the result is larger than the uncovered portion, the Field generator applies.
(1/8 missing requires 3+, 7/8 missing requires 10)

\begin{tabular}{c|cccccc}
    Type & Protection &Weight& Cost & Failure  & Reboot & Coldboot \\
    \hline Basetech\\
    Applique-Armor & Strength 1 & 1 & - & destroy, block & - & permanent \\
    \hline Lowtech\\
    Basic Deflector & 1 Evasion & 0.2 & 10E/r, 1H/attack & - & - & 5E, 1r, Config 5\\
    Basic Dampener & 5 + Config Reduction & 0.5 & 20E/r, 3H/attack & - & - & 30E, 3r \\
    \hline Midtech\\
    Shield & Strength 3 & 1 & 40E/r or 10E/r, 1H/attack & passthrough & 5r & 2000E \\
    Complex Deflector & 3 Evasion & 0.8 & 40E/r, 2H/attack & - & - & 160E, 8r, Config 10\\
    Heavy Dampener & 30 + Config\(\times 3\) Reduction & 1 & 60E/r, 5H/attack & - & - & 100E, 10r\\
    Flash Shield & Strength 1 & 1 & 20E/r), 2H/attack & block & X\(\times\)50E & 200E, 2r\\
    \hline Hightech\\
    Advanced Shield & Strength 4 & 1 & 200E/r or 20E/r & block & 1r & 5r
\end{tabular}

\vspace{1cm}

\textbf{Deflectors} need to be Configured with the Deflector skill and require a minimum degree of success to
work and provide flat evasion-level bonuses.

\textbf{Dampeners} need to be Configured with the Shield skill and provide a flat damage reduction to all
attacks that are influenced by shields, they usually scale with the Quality of the Configuration.

\textbf{Flash Shield} As soon as the Reboot Energy is paid and the configuration is done, they turn back on.
X is set to 0 at Coldboot and increased by 1, everytime the Shield is broken.
A 10-Resonance on the Configuration reduces X by that much, even going negative.
While X is negative, the Energycost is 0.

Cost: per sector for being active.

Failure: Normal behaviour on Failure is for the shield to turn off until rebooted.

Dampeners and Deflectors dont fail from damage.

\subsection{Armor}\label{subsec:armor}
\begin{tabular}{c|ccc}
    Type & Strength & Weight & Failure\\
    \hline BaseTech&&&\\
    Outside Cargo & 0 & 1.1 & destroyed, passthrough\\
    Metal Plating & 2 & 2 & damaged, passthrough\\
    Ultra High Density Composite & 4 & 5t & out of order, block\\
    \hline Lowtech &&&\\
    Sheetmetal & 0 & 0.1 & passthrough \\
    Composite & 3 & 2.5 & damaged, passthrough \\
    \hline Midtech &&&\\
    Active & 1/4 & 2 & out of order, passthrough full/1\\
    SpeedShell & 1 & 0.5t & destroyed, passthrough \\
    \hline Hightech &&&\\
    Ion & 5 & 1 & destroyed, energy system damage, block \\
    \hline Experimental &&&\\
    Holomatrix & 1 & 0 & damaged\\
\end{tabular}

\begin{enumerate}[label = - ]
    \item Outside Cargo: Provides flat reduction depending on cargo.
    Cargo gets destroyed.
    \item Metal Plating: Repairs need 12 or more to not lower Quality
    \item Ultra High Density Composite: Repairs need 8 to succeed and Freq1 Resonance lowers Strength by Amp
    \item Composite: needs to be replaced, spare parts 200kg, success with 6+, scrap at 2
    \item Active: needs 2E per round and per incoming hit or Strength is 1.
    Repairs Success with 15+/Spare 5+, 1--4 Scraps the Layer, Freq1 subtracts
    \item Speedshell: Vent 1H per 5m/s;
    Repair 12+, 1--11 Scraps the Layer
    \item Ion: 4E/r per Segment, on destruction energy Output is reduced by 10\% until scrapped armor is removed.
\end{enumerate}

