\subsection{Biotech}\label{subsec:biotech}
Biotech is the Fusion of Biology and Technology \par
The ancient texts define Biotechnology as "any technological application that uses biological systems, living organisms,
or derivatives thereof, to make or modify products or processes for specific use".
\begin{enumerate}[label= -]
    \item \textbf{Red} Biotechnology Encompasses genetics, genomics, pharmacology, but also medical advances like
    genetherapy and automedics and deconamination of living things.
    \item \textbf{Green} Biotechnology is used every time the passive environment is exploited,
    from engineering high yield, low footprint farming to technologically harnessing the great and small Anomalies,
    including detoxification of materials and beings.
    \item \textbf{Blue} Biotechnology has developed from being used for aquatic Biotech, to include Megafauna, since the
    first Megafauna is told to having been spottet in the ocean.
    It allows scanning, categorization and assessment of Megafauna, including in some cases,
    harvesting Megafauna specialities.
    \item \textbf{White} or Industrial Biotechnology  is used in Industrial processes and in handling some of the
    results of such processes.
    Creating and applying contamination-sealant is one of such processes.
    \item \textbf{Black} deals with with integration of Biology and Technology from enhancements or replacements like
    Cyberware or more conventional Prosthetics to synthesizing life, ressurection and strong AI. Seldomly useful
    and the most dangerous brand of Biotechnology, it is not taught often.
\end{enumerate}
\subsection{Computer}\label{subsec:computer}
\begin{enumerate}[label= -]
    \item \textbf{Programming} 
    \item \textbf{Usage} 
    \item \textbf{Hacking} 
\end{enumerate}
\subsection{Engineering}\label{subsec:engineering}
\begin{enumerate}[label= -]
    \item \textbf{Repair} 
    \item \textbf{Design} 
    \item \textbf{Build} 
\end{enumerate}
\subsection{Aux}\label{subsec:aux}
\subsubsection{Defense}
\begin{enumerate}[label= -]
    \item \textbf{Decoys}
    \item \textbf{Shields}
    \item \textbf{Deflectors}
\end{enumerate}
\subsubsection{Offense}
\begin{enumerate}[label= -]
    \item \textbf{Explosives}
    \item \textbf{Sniping}
    \item \textbf{Gadgets}
\end{enumerate}
\subsubsection{Recon}
\begin{enumerate}[label= -]
    \item \textbf{Scanners}
    \item \textbf{Suppressors}
    \item \textbf{Sabotage}
\end{enumerate}
\subsubsection{Utility}
\begin{enumerate}[label= -]
    \item \textbf{Communications}
    \item \textbf{Reprocessing}
    \item \textbf{UtilityMovement}
\end{enumerate}
\subsection{Metal}\label{subsec:metal}
\subsection{Ceramics}\label{subsec:ceramics}
\subsection{Leatherworking}\label{subsec:leatherworking}
\subsection{Boneworking}\label{subsec:boneworking}
\subsection{Woodworking}\label{subsec:woodworking}
\subsection{Woodcraft}\label{subsec:woodcraft}
\subsection{Animalcare}\label{subsec:animalcare}