\section{Sizes}\label{sec:sizes}

\begin{tabular}{r|ll}
    Sectors &Mechclass & Weight\\
    0.5 &Human & 0.1t\\
    1--2 &Exo& <1t\\
    3--4 &Tiny & 1--5t\\
    5--6 &Very Light& 5--15t\\
    6--7 &Light& 15--50t\\
    8--9 &Medium& 50--150t\\
    10--11 &Heavy& 150--500t\\
    12--15 &Very Heavy& 500--1500t\\
    16+ &Ultra& >1500t\\
\end{tabular}\par
Modules are assigned to sectors.
Each sector has a size of 1, a module takes up some of that size.
Modules can be spread over multiple Sectors, as long as they are adjacent, although this will increase the likelyhood
of it sustaining damage.
Some Modules require a Hardpoint, there is generally only one Hardpoint per Sector.\par
A Mech has an effective Tech Level of the Tech at the 90\% point of the sizes modules ordered by Tech Level.\par
Contamination Damage applies to the highest Tech modules first.
Each Module can be damaged individually.\par
\section{Systems}\label{sec:systems}
A Mech needs a movement system, energy and heat systems and should probably have a seal, weapons and support systems.
\subsection{Costs}\label{subsec:costs}
Systems Examples\par
\begin{tabular}{c|c|l}
    Tech    & Credits Cost    & Examples\\
    B    &    4        &    \makecell*[{{p{12cm}}}]{Water Destillery, Rail based movement system, simple wheels,
    Manned gun, Ramshield, Floatation,   Metal Armorplating , Extra Cargo (10), steam engine, passive cooling}\\&&\\
    L    &    5        &    \makecell*[{{p{12cm}}}]{Lowtech Detox-Decon Equip(LDDE; +1), suspended wheels, tracks,
    bipedal, Dynamo , Autoturret, Jumpjets, Mech sized Sword, water cooling circle, basicHeatsink }\\&&\\
    M    &    6        &    \makecell*[{{p{12cm}}}]{Shields, flexible/balanced bipedal, Boostjets,
    Deployable Solar Panel, Sensorarray,  MDDE (+2), Base AI system, Mech sized Weaponry (Advanced
    (Vibro/electro/Monofilament) Sword), Rocketlauncher, Water venting system, midtech Heatsink}\\&&\\
    H    &    7        &    \makecell*[{{p{12cm}}}]{BCI, Advanced AI, WeaponLaser, Sustained Flight,  Advanced
    Shields, Nano Repair Cloud, Automedic, OVERDRIVE mode, Hightech Heatsink}\\&&\\
    E    &    8        &    \makecell*[{{p{12cm}}}]{Quantum Lookahead Sensors, Blink Teleporter, Timerift Shields
    (Delays Damage 1d10 rounds), EnergySword}
\end{tabular}\par
Designtarget (TODO: write words good) for normal fighting mech

\begin{enumerate}[label = - ]
\item 20\% movement
\item 20\% weaponry
\item 5\% energy
\item 5\% Cargo
\item 50\% + armor
\end{enumerate}


\subsubsection{Energy Systems}\label{sec:energy-systems}
Energy Systems usually do not use a hardpoint.
\paragraph{Power to Weight} is how much maximum output power per weight the system provides.
\paragraph{Input} of an Energy System is generally considered its "fuel", but can also just be batteries or similar.
The Input is stored with other Cargo.
\paragraph{Output} are "Modes".
They each provide an energy budget for the mech, different Situations might warrant different modes,
generally there are 2:
low power mode where the range is maximized (running at 5%) and
high power mode, where the output is maximized.
\paragraph{Efficiency} is the rate at which Input is consumed per mode.

\begin{tabular}{l|cccll}
    Type & kw per t & heat/r per t & modes & input & efficiency\\
    \hline Basetech \\
    Steampower & 3.5 & 8 & 100\%/25\% & Coal & 5\%/10\%\\
    FlyWheel & 100 & 0 & scalable & stored & loses 10\% per turn \\
    Crank & 10--500/human & 0 &scalable&Labor&-\\
    \hline Lowtech \\
    Combustion Motor& 700 & 2 & 10\%  & Combustible & 40\% \\
    \hline Midtech \\
    PEM & 500 & 0.1 & 1 & HFC & 90\% or HFC\\
    Solar Panel & 50 & 2 & On/Off & Sunlight & Contamination dependent\\
    \hline Hightech \\
    Reactor & 1500 & 0.5 & 100\%--10\% & Fuelrods & 80\%\\
    Capacitor & 400kJ & 0.1 & in/out & electricity & loses 10\% per hour \\
\end{tabular}

\paragraph {HFC-10} 10 liter - hydrogen fuel cell: Cylinder 20cm diameter,
35 cm height or 23cm cube=10L, containing 9 MJ
\paragraph {HFC-50} 50 liter - hydrogen fuel cell: Cylinder 40cm diameter,
40 cm height or 37cm cube = 50L, containing 45 MJ
contains low power sub system
used to power up basic systems (like hydrogen gas pumps for the PEM Stacks)

\paragraph {Solar Panel} Deploying takes 5 turns times 100w or 5 minutes labor, any damage received while deployed
will also damage the Solar panel, production halved every 5 contamination levels, only works during day

\subsubsection{Movement Systems}\label{sec:movementsystems}
\paragraph{Efficiency} is the ratio of power consumed to power used to move the mech
\paragraph{Drag} is the general amount of power wasted the faster the mech is going
\paragraph{Power to Weight} is how much maximum movement power the system can employ per weight

\begin{tabular}{l|cccccl}
    Type    & Efficiency & Drag & Power to Weight & hardpoints &Extra\\
    \hline
    Basetech\\
    railbased            & 95\%& 0.8 & 500 & 1--50\%--4 & rails \\
    simple wheels        & 75\% & 1 & 750 & 25\% & flat terrain \\
    floatation system    & 90\% & 20 &  90 & 10\% & water\\
    \hline
    Lowtech\\
    complex wheels       & 80\% & 0.4 & 1500 & 25\% &  somewhatflat terrain \\
    tracks               & 30\% & 15 & 300 & 33\% & rough terrain\\
    bipedal              & 50\% & 2& 100 & 25\% & all terrain\\
    jumpjets             & 10\% & 1 &1000 & 1 & upwards\\
    \hline
    Midtech\\
    flexible bipedal     & 60\% & 1.8 & 150 & 25\% &  like a large human\\
    boostjets            & 20\% & 1 & 1500 & 2 &  any direction\\
    \hline Hightech\\
    Spiderwalker         & 40\% & 2 & 400 & 50\% & any surface\\
\end{tabular}\par

Accelleration is noted down as 5 steps in 5 second intervals each (calculated from mech weight and power)

\subsubsection{Heat Systems}\label{sec:heat-systems}
Warning: ALL Dissipated heat contributes to IR signature
\paragraph{Input} is the amount of power the Heat System requires to function actively
\paragraph{Weight} direct weight of the system
\paragraph{Cooling} how much heat is dissipated, passively/actively.
\paragraph{Capacity} how much heat can be stored in this system.
Cumulative for the mech.

\begin{tabular}{r|lllll}
    Type & Input & Weight & Cooling & Capacity &Extra\\
    \hline Basetech\\
    Small Heatsink & 0 & 0.5t & 0.2 & 15 & Storage\\
    \hline Lowtech\\
    Radiator Vent & 10kw/t &scalable & 1/t / 5/t & 1 Hardpoint\\
    Large Heatsink & 0 & 1t & 0.5 & 50 &Storage\\
    \hline Midtech\\
    Optimized heatsink  & 0 & 1t & 1 & 80 &Storage\\
    Coolant Dump  & 1MJ & 4t & 0/100 & 100 &Decoy\\
    Radiator Wings & 1kw & 2t & 10\% & 100 & Deploy\\
    \hline Hightech\\
    Fractal heatsink & 0/1kw & 2t & 3/0 & 200 & Storage\\
    OVERDRIVE & 5MJ & 1t & 0 & Gadget\\
\end{tabular}\par

\paragraph{Coolant Dump}: When triggered, releases 100 stored heat together with 100L water, as a thermal barrier
\paragraph{Radiator Wings}: Deploying takes 5 turns times 1kw or 5 minutes labor, any damage received while deployed
will also damage the Radiator Wings: radiates 10\% of total system heat, as long as 1kw  energy (for coolant pumping)
is applied.
\paragraph{Overdrive}: When triggered, enter overdrive mode: able to act at double speed,
stored heat is spent insteadof gained.
When heat drops to 0 or below, Mech shuts down for 2d10 rounds and Overdrive requires a Competence, Gadgets-Repair;
10m;
Threshhold of 10 to repair.

\subsubsection{Seals}\label{subsubsec:seals}
\paragraph{Level} how much the seal reduces Contamination behind it.
\paragraph{Resistance} how much damage it takes to damage the Seal.

\begin{tabular}{l|r|r|r}
    Tech & Seal Level & Resistance & Cost/Sector\\\hline
    Base &  6 & 2 & 1\\
    Low &   13& 3 & 2\\
    Mid &   21& 4 & 3\\
    High &  30& 5 & 4\\
    Experimental& 50 & 2 &8\\
\end{tabular}\par

\subsubsection{Weapons}\label{sec:weapons}
\paragraph{Damage}
\paragraph{Threshholds}
\paragraph{Costs}
\paragraph{Skills}

Melee weapons rely on the movement System, so their costs are in meters that are used to attack rather than move\par
\begin{tabular}{c|clll}
    Type & Damage & Threshholds & Costs & Weight\\
    \hline BaseTech&&&&\\
    Metal Sword & 10 & 10m[5,7,9,11,13,15,17,19,20]0 & 30m & 5t \\
    Manned Turret & X & X & \makecell[l]{manual \\labor +X} &  X +50\% \\
    \hline Lowtech &&&&\\
    Heavy Machinegun & 3 & \makecell[l]{100m[3,6,10,14,18]20\\
                                        500m[5, 8, 12,15]10\\
                                        1000m[7,10,14]5\\
                                        2km[11,16]5\\
                                        8km[15]1 indirect}
                                            & 5kg, 5H & 100kg \\
    Light Artillery & 12 & \makecell[l]{7km[8,12,16,20]1 \\
                                        15km[10,14]}& 50kg, 10H & 8t  \\
    120mm Smoothbore & 14 & \makecell[l]{50m[10,20]3\\
                                        100m[6,10,14]8\\
                                        500m[5,7,9,11]15\\
                                        2km[8,10,12,14,16]20\\
                                        4km[11,13,15,20]10 indirect\\
                                        8km[13,17]5 indirect}
                                            & 20kg 5H & 20t \\
    \hline Midtech &&&&\\
    Autocannon & 8 & \makecell[l]{10m[10]3\\
                                  200m[5,8,11,14,17,20]15\\
                                  1km[8,12,16,20]20\\
                                  2km[10,14,18]10 \\
                                  4km[13,17,20]5 indirect }
                                        & 7kg 5H & 5t \\
    Pulse Laser & 6 & \makecell[l]{1km[5,6,7,8,9,10,11,12,13,14,15]50\\
                                   5km[7,9,11,13,15]100\\
                                   LOS[10,12,14,16,18]100}
                                        & 5MJ 10H & 7t\\
    Precision Cannon & 15 & \makecell[l]{500m[7,10,13]2\\
                                         2km[7,8,9,10,11,13,15,17,19]30\\
                                         LOS[8,10,12,14,16,18,20]25}
                                        & 15 kg 10H & 10t\\
    Rocket Launcher x 8 & X & X & X & 500kg \\
    \hline Hightech &&&&\\
    Rocket Platform & X & X & X & 1500 kg \\
    Railgun & 16 & \makecell[l]{200m[7,9,11,13,15]5\\
                                1km[5,7,9,11,13]10\\
                                4km[7,9,11,13,15]5\\
                                12km[9,11,13,15,17]1}
                                & 50 kg, 25H & 15t\\
    Advanced Pulse Laser & 9 & \makecell[l]{3km[5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20]50\\
                                   9km[7,9,11,13,15,17]100\\
                                   LOS[10,12,14,16,18]100}
                                        & 9MJ 15H & 3t\\
    Ramping Beam Laser & X & \makecell[l]{1km[5,10,15]10\\
                                          LOS[10,15]100}
                        & X\(\times\)(50kw 1H) & 10t\\

\end{tabular}\par

\paragraph{Notes}:
\begin{enumerate}[label = - ]
\item Melee Weapons: Ignore Shields\\
\item Manned Turret: X Depends on the mounted gun and the skill of the gunner\\
\item Light Artillery: Attacks take 1s per 300m distance, rounded up, minimum range 100m\\
\item 120mm Smoothbore: Can only fire every second round, requires Indirect for targets further away than 2k\\
\item Autocannon: may make another attack instantly for double the cost\\
\item Basic Pulse Laser: -0.1*contamination level dmg per km, rounded mathematically \\
\item Precision Cannon: Needs to be stationary to aim and fire, 1 turn of aiming between shots \\
\item Rocket Launcher: Ignores Shields \\
\item Rocket Platform: Ignores Shields, Beam rules \\
\item Railgun: Needs to be stationary to fire.
Loading takes 2 turns.\\
\item Advanced Pulse Laser: -0.1*contamination level dmg per km, rounded mathematically \\
\item Ramping Beam Laser: Every round, X increases by 1 while shooting, decreases by 1 down to 0 otherwise.\\
\end{enumerate}

\section{Support}\label{sec:support}
shields and coffee machines blurgh

\section{example}\label{sec:example}
100t, 8 sectors

5 t Power: 20--500kw/t => 2.5MW, Input HFC50 (4KG),
2.5 MW: 10 seconds at maximum load, efficiency 55\%
100 kw, 7 minutes at minimum load, efficiency 93\%
20t Movement: Efficiency 40\%, Drag: 1, 30 kw/t
(100t => full power 9,13,16,30, 2000MW)
25\%--
8sectors*3layers*2t armor = 48t
73\%--
5t 120mm smooth
5t 50 mm auto
83\%--
cargo
heat
supportsystems



\section{Shieldsystems}\label{sec:shieldsystems}
\begin{tabular}{c|cccccc}
    Type & Protection &Weight& Cost & Failure  & Reboot & Coldboot \\
    \hline Basetech\\
    Applique-Armor & Strength 1 & 1t & - & destroy, block & - & - \\
    \hline Lowtech\\
    Basic Deflector & 1 Evasion & 0.2t & 10kW/50kW;
    1H/attack & - & - & 1r\\
    Basic Dampener & 1 Reduction & 0.5t & 50kw/100kw;
    3H/attack & - & - & 3r \\
    \hline Midtech\\
    Shield & Strength 3 & 1t & 200kw/50kw;
    1H/attack & passthrough & 5r & 10MJ \\
    Complex Deflector & 3 Evasion & 0.8t & 100kw/200kw;
    2H/attack & - & - & 8r\\
    Heavy Dampener & 5 Reduction & 1t & 50kw/300kw;
    5H/attack & - & - & 10r\\
    Flash Shield & Strength 1 & 1t & 500kw/100kw;
    2H/attack & block & 0.5MJ & 2r\\
    \hline Hightech\\
    Advanced Shield & Strength 4 & 1t & 1MW/ 100kw & block & 1r & 5r \\
\end{tabular}\par

Strength like armor
Cost:  per sector of armor for Charging/Active states, per round\par
Failure: Normal behaviour on Failure is for the shield to turn off until rebooted.
Dampeners and Deflectors dont fail from damage.

\section{Armor}\label{sec:armor}
\begin{tabular}{c|ccc}
    Type & Strength & Weight & Failure\\
    \hline BaseTech&&&\\
    Outside Cargo & 0 & 1.1t & destroyed, passthrough\\
    Metal Plating & 2 & 2t & damaged, passthrough\\
    Ultra High Density Composite & 4 & 5t & out of order, block\\
    \hline Lowtech &&&\\
    Composite & 3 & 2.5t & damaged, passthrough \\
    \hline Midtech &&&\\
    Active & 1/4 & 2t & out of order, passthrough full/1\\
    SpeedShell & 1t & 0.5t & destroyed \\
    \hline Hightech &&&\\
    Ion & 5 & 1t & destroyed, energy system damage, block \\
\end{tabular}

\begin{enumerate}[label = - ]
    \item Outside Cargo: Provides flat reduction depending on cargo.
    Cargo gets destroyed.
    \item Metal Plating: Repairs need 12 or more to not lower Quality
    \item Ultra High Density Composite: Repairs need 8 to succeed and Freq1 Resonance lowers Strength by Amp
    \item Composite: needs to be replaced, spare parts 200kg, success with 6+, scrap at 2
    \item Active: needs 10kW per round per incoming hit or Strength is 1.
    Repairs Success with 15+/Spare 5+, 1--4 Scraps the Layer, Freq1 subtracts
    \item Speedshell: Vent 1H per 10m/s;
    Repair 12+, 1--11 Scraps the Layer
    \item Ion: 20kW per Segment, on destruction energy Output is reduced by 10\% until scrapped armor is removed.
\end{enumerate}

\section{Misc Modules}\label{sec:miscmodules}
\par
\subsection{Basetech}\label{subsec:basetech}
\subsubsection{Water Distillery}\label{subsubsec:water-distillery}
Energy Cost: 200kw\par
Heat: 10\par
Weight: 0.5t\par
Turns 4L of Dirty Water into 4L of Contaminated Water per minute\par
Requires Reprocessing 1 to use\par

\subsubsection{Cargo compartment}\label{subsubsec:cargo-compartment}
stores up to 1 t of Cargo\par
Weight: 0.5t for Size Calculation, Empty weight 0.1t, Full 1.1t for speed calculation
\par
\section{Lowtech}\label{sec:lowtech}
\subsubsection{Basic Food Processor}\par
Energy Cost per operation: 1800 (3e/s)\par
Heat: 5/s \par
Size:0.5\par
Detoxes 1kg of Food in 10 minutes \par
Requires Detox Rating of 2\par
\par
Basic Air Filter\par
Energy Cost per operation: 2400 (4/s)\par
Heat: 2\par
Size:0.5\par
Decontaminates and pressurizes 5000 L of air in  10 minutes or double without pressurizing. \par
Requires Decon 1\par
\par
Basic Decon Equipment \par
Energy Cost per operation: 18k (5/s)\par
Alacast Cost per operation: 10g\par
Heat: 10 \par
Size: 0.5\par
Allows to turn Contaminated Objects into uncontaminated objects at the rate of 10kg/h, if suitable\par
Required Decon 2\par
\par
Optical Sensors\par
Energy: 1\par
Size: 0.25 \par
Rating: 100\par
Provides Targetting Lock is obtained\par
Visual Lock: Distance/Rating <= Target Size (+Camouflage and visual impairments)\par
\par
Thermal Sensors\par
Energy: 1\par
Size 0.25\par
Rating 100\par
Thermal Lock: Distance/Rating <= Target Thermal Signature\par
\par
Basic Computer System\par
Size: 0.5\par
Energy: 0.1\par
Module: Processor or Memory\par
\par
\section{Midtech}\label{sec:midtech}
ComputerSystem:
Size: 0.1
Energy: 0.1
Module: Processor or Memory\par
\par
Nondeterministic Computation Core:\par
Size 0.5\par
Energy: 0.5\par
Module: Processor\par
Requires Black Biotech 3\par
\par
Extended Decon Equipment\par
Energy Cost per Operation: 36k (10/s)\par
Alacast Cost per Operation: 5g\par
Size: 1
Allows to turn Contaminated Objects into uncontaminated Objects at the rate of 100kg/h if suitable\par
If used on Humans, Roll Red Biotech, on 9 or more, removes one Charactertaint.\par
Always Inflicts Wound of Level 11-RollResult\par
Requires Decon 3\par
\par
Extended Detox Equipment:\par
Energy Cost per Operation: 36k (10/s)\par
Size 0.75\par
Allows Detoxing and Preparing of up to 1t/h\par
If used on Humans, Roll Red Biotech, on 6 or more, remove all Infections and appropriate Toxins.\par
Always Inflicts Wound of Level 8-RollResult\par
Requires Detox 3\par
Automedic:
Energy Cost: 6k(variable - 10/s for 10 min)\par
Size: 0.75\par
Supplies tools of Medic/ supplies good operating conditions for Medic / reduces the use of Medicine by half / allows stasis\par
Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
double Advantage or autonomously attempts the procedure at Level 3 mod -1.\par
If not, Instead supplies one Advantage.\par
Software may supply the Red Biotech roll even autonomously.\par
Stasis is automatic and slows down the daily/hourly tickrate (including Healing and Contamination) by a factor of 10
(additive) for every energy point per second.
This is a medical coma, not timedilation.
\section{Hightech}\label{sec:hightech}
Advanced Detox-Decon Equipment \par
Size: 1\par
Energy Cost per Operation 72k (variable 20/s for 1 h)\par
Alacast Usage per Operation if Detainting: 1g/t of raw material, 10g/human\par
Detoxes and Detaints up to 5t of material, including air and water.\par
Living Entities suffer no harm, and on a 4 or more on a Red Biotech Roll lose one Taint level.
Furthermore all Infections and Appropriate Toxins are removed.\par
Requires Detox 4 and Decon 4\par
\par
Advanced AutoMedic\par
Energy Cost: 3k (variable - 5/s for 10 min)\par
size: 1\par
Allows Medic Rolls/ supplies very good operating conditions for Medic Rolls/ reduces the use of Medicine by 90\%/allows Ressurection\par
To Treat a wound:\par
Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
triple Advantage or autonomously attempts the procedure at Level 4 mod -1.\par
If not, Instead supplies one Advantage or autonomously attempts the procedure at Level 2.\par
Software may supply the Red Biotech roll even autonomously.\par
To Ressurect:\par
requires 1g of EOL per total spent points on a character (or 20* the average level of an NPC)
Roll Black Biotech, every 15\% missing from the corpse or order of magnitude in days that has passed since the time of death
lowers the final score by 1.
If the roll succeeds, place 5 wounds of severity 15-result on that character, they lose
one level from the highest Ability and one from the highest Skill and are alive again.
If the roll does not succeed,
5\% of the total corpse and the dosage of EOL is lost.

