    \subsection{The Selector System}\label{subsec:selectorsystem}
    This System uses  ten sided dice.
    A Check is a roll of usually 5 dice interpreted in a certain way,
    with the result describing how successfull the attempted action was.\par
    Whenever there is advantage or disadvantage of any kind,
    \hyperref[subsec:bonus--and-penaltydice]{Bonus- or Penaltydice} may be applicable.
    The Roll itself is interpreted by your \emph{Selectors} which usually are defined
    by the applicable Attribute and Skill, but may be static, or Equipment based.
    The Dice in the Roll are ordered and given an order-number in ascending order by value.
    To get the Result of the Roll (or to \emph{interpret} the roll), every selector \emph{selects} a die with the
    appropriate order-number and adds them to the result.
    Selectors greater than the biggest order-number simply select the highest die.
    A Selector of 0 selects no die.
    The usual number of Selectors is 2.\par
    The effects and result of the Check may then be further modified by \hyperref[subsec:resonance]{Resonance}.
    \vspace{1cm}

    \subsection{Bonus- and Penaltydice}\label{subsec:bonus--and-penaltydice}
    Bonus and Penaltydice cancel each other out, so 3 Bonusdice and 2 Penaltydice results in 1 Bonusdie.\par
    They describe how many extra dice are rolled on a given Roll.
    If Bonusdice were rolled,
    remove the lowest dice from the Roll until the number of dice is as it was before the extra dice.
    For Penaltydice, the highest are removed instead.
    Neither Bonus nor Penaltydice ever change the number of dice being interpreted, just the relative Chances.

    \subsection{Resonance}\label{subsec:resonance}
    Resonance is when in a Roll, more than one die, show the same Number.\par
    The Resonance \emph{amplitude} is the number of dice \emph{that exceed 1}, meaning it is lower by 1 than the
    number of dice.\par
    The Resonance \emph{frequency} is the number those dice show.
    If no Effect states anything about a Resonance, they have no effect.

    \subsection{Skills and Attributes}\label{subsec:skillsAndAttributes}
    Attributes represent in what aspects of the gameworld a character excels and in which he doesnt.\par
    Depending on the Priorities picked during character creation it may be easier or harder to raise them, but every
    Attribute can be Applied to a multitude of general Actions, see the examples in the table below.\par
    The Priorities and Attributes in the following Table are a not all that exist
    but they are the most common Attributes shared by all humans.\vspace{1cm}
    \begin{tabular}{l||cccccc}
        Priorities      &Charisma      &Wisdom         &Body        &Ability    \\\hline\\
                        &Resolve       &Perception     &Fitness     &Competence   \\
        Attributes      &Impression    &Mind           &Dexterity   &Insight   \\
                        &Sympathy      &Knowledge      &Agility     &Theory   \\



    \end{tabular}\vspace{1cm}
    \subsubsection{Charisma Attributes}
        \begin{enumerate}[label= -]
            \item {Resolve}: reasoning, convincing, bartering, negotiating and similar interactions
            \item {Impression}: leadership, bluffing, acting, boasting, lieing
            \item {Sympathy}: chatting, pleading, resolving conflicts, being likeable
        \end{enumerate}
    \subsubsection{Mental Attributes} 
        \begin{enumerate}[label=-]
            \item {Perception}: gathering information, noticing details, being alert
            \item {Mind}: memory, assessing situations, processing information, menial mental tasks
            \item {Knowledge}: knowing, learning, posessing and storing information
        \end{enumerate}
    ////////////TODO:REWORK
    \subsubsection{Physical Attributes} 
        \begin{enumerate}[label= -]
            \item {Fitness}: general physical actions, applying strength, persisting, healing
            \item {Dexterity}: precise and/or speedy manipulation of objects using hands
            \item {Agility}: running, jumping, dodging, climbing
        \end{enumerate}
    \subsubsection{Ability Attributes}
        \begin{enumerate}[label= -]
            \item {Competence}: repetetive or physically complicated actions
            \item {Insight}: creative or explorative actions
            \item {Theory}: applying knowledge or mentally complicated actions
        \end{enumerate}
    \subsubsection{Tech Attributes}
        \begin{enumerate}[label= -]
            \item {Usage}: How to handle and operate complicated (or unknown) technology.
            \item {Analysis}: Gathering information about the workings and purposes of complicated or unknown technology
            \item {Integration}: Wiring/interfacing technology together that might or might not have been build for
            that purpose.
        \end{enumerate}
    \subsubsection{Spiritual Attributes}
        \begin{enumerate}[label= -]
            \item {Harmony}: bringing spirits and self into harmony
            \item {Eminence}: the power to reach higher status among spirits
            \item {Unity}: the ability to entwine wills of spirit and self
        \end{enumerate}
    \subsubsection{Weapons Expertise}
        \paragraph{Laser}s or technically "Directed Energy Weapons" \par are a group of weapons which typically
    do not use Ammunition, but raw Energy to inflict their damage.
    Their comparably low damage is made up for by being
    as accurate as a light beam.
    Plus the high amounts of particles in the air make for pretty lights.
        \begin{enumerate}[label= -]
            \item {Pulse} Weapons that emit short, sometimes repeated pulses of energy, mostly to save on heat, but also
            to be able to use special capacitors to deliver powerful bursts of energy.
            \item {Beam} Weapons that emit long, sometimes even sustained streams of energy, making them easier to aim
            and inflicting more damage, usually at the price of higher sustained energy and heat costs.
        \end{enumerate}
        \paragraph{Projectile} Weapons or sometimes just "Guns" \par are a group of weapons which discharge Projectiles
        towards a target.
        Ammunition has to be employed, but there are several different types available.
        \begin{enumerate}[label= -]
            \item{Direct} Projectile Weapons are many and varied but share the characteristic of being pointed roughly at
            the target they are shooting.
            They require line of sight.
            \item{Indirect} Projectile Weapons are just as varied as Direct Projectile Weapons but have the key difference
            of not pointing at the target.
            Usually Up in an angle.
            They require information about the targets position,
            but are free from line of sight restrictions the Projectile still has to have a valid way to travel to be used.
        \end{enumerate}
        \paragraph{Missile} Weapons \par are a weapons that travel to the target to inflict damage, the difference
        to Projectile Weapons is that Missile Weapons are usually self propelled instead of being accelerated at their
        startpoint.
        Missiles are comparatively heavy and expensive, but most of them ignore shields and/or deliver
        special devices or bombs to the target.
        \begin{enumerate}[label= -]
            \item{Seeking} Missiles have some sort of sensors or a dataconnection, and will follow a Target, as long as the Lock
            remains unbroken.
            \item{Dumbfire} Missilies dont spend that much on electronics besides a flight stabilizer so they are
            harder to shoot down, but evadeable.
        \end{enumerate}
        \paragraph{Melee} Weapons of mech sizes \par are capable of inflicting utter destruction, but are usually
        limited to close ranges, which makes them not very useful at long distances.
        \begin{enumerate}[label= -]
            \item{Sharp} Melee Weapons have slightly longer range or are faster and usually do good damage.
            Most of them
            use the Movement System to get ready to attack again, so they may attack a lot of times on fast mechs.
            They also are the most precise of the melee weapons.
            \item{Blunt} Melee Weapons are usually slow, and easier to dodge, but their raw damage output is only
            matched by Artillery.
            \item{Unarmed} is not technically a category of weapon, but it represents being able to fight in melee
            without any special weapon, which allows for mostly disabling maneuvers.
        \end{enumerate}
    \subsubsection{Piloting Practice}
        \paragraph{Exo} is short for "Exoskeleton" and refers to Mechs that are barely larger than an extended Bodyarmor
        or Mechs that are generally not much bigger than their Pilot.
        \paragraph{Tiny} a versatile spot for Contraptions between Exo and Very Light, these include buggies, cars and
        a lot of small, fast Vehicles.
        \paragraph{Very Light} include things like APCs and small fast walkers.
        \paragraph{Light} is about as big as a medium tank.
        \paragraph{Medium} is about as big as a heavy tank/main battle tank.
        \paragraph{Heavy} is equivalent to superheavy tanks.
        \paragraph{Very Heavy} LANDKREUZER
    \subsubsection{Aux}
        \paragraph{Biotech} is the Fusion of Biology and Technology \par The ancient texts define Biotechnology as
        "any technological application that uses biological systems, living organisms, or derivatives thereof, to make
        or modify products or processes for specific use".
        \begin{enumerate}[label= -]
            \item{Red} Biotechnology Encompasses genetics, genomics, pharmacology, but also medical advances like
            genetherapy and automedics and deconamination of living things.
            \item{Green} Biotechnology is used every time the passive environment is exploited, from high yield,
            low footprint farming to harnessing the great and small Anomalies, including detoxification of materials and
            Beings.
            \item{Blue} Biotechnology has developed from being used for aquatic Biotech, to include Megafauna, since the
            first Megafauna is told to having been spottet in the ocean.
            It allows scanning, categorization and
            assessment of Megafauna, including in some cases, harvesting Megafauna specialities.
            \item{White} or Industrial.
            It is used in Industrial processes and in handling some of the results of such
            processes.
            Creating and/or applying contamination-sealant is one of such processes.
            \item{Black} deals with with integration of Biology and Technology from enhancements or replacements like
            Cyberware or more conventional Prosthetics to synthesizing life, ressurection and strong AI. Seldomly useful
            and the most dangerous brand of Biotechnology, it is not taught often.
        \end{enumerate}
    \pagebreak
    \subsubsection{Skilltree - Techside}
    Further Priorities might include Attributes, single Skills or Entire Skilltrees.
    A number in brackets indicates how many
    Skillpoints can be assigned, lacking a number implies being either a category (nodes) or an Attribute (leaves).
    \dirtree{%
    .1 Skills.
    .2 Tech Attributes.
    .3 Usage.
    .3 Analysis.
    .3 Integration.
    .2 Mech Skills.
    .3 Weapons Expertise.
    .4 Laser.
    .5 Pulse.
    .5 Beam.
    .4 Projectile.
    .5 Direct.
    .5 Indirect.
    .4 Missile.
    .5 Seeking.
    .5 Dumbfire.
    .4 Melee.
    .5 Sharp.
    .5 Blunt.
    .5 Unarmed.
    .3 Piloting Practice.
    .4 Exo.
    .4 Tiny.
    .4 Very Light.
    .4 Light.
    .4 Medium.
    .4 Heavy.
    .4 Very Heavy.
    .4 Ultra.
    .3 Auxilliary Training.
    .4 Defense.
    .5 Decoys.
    .5 Shields.
    .5 Deflectors.
    .4 Offense.
    .5 Explosives.
    .5 Sniping.
    .5 Speciality Gadgets.
    .4 Recon.
    .5 Scanners.
    .5 Suppressors.
    .5 Sabotage.
    .4 Utility.
    .5 Communications.
    .5 Reprocessing.
    .5 Utility Movement.
    .4 Biotech.
    .5 Red.
    .5 Green.
    .5 Blue.
    .5 White.
    .5 Black.
    }
    \pagebreak
    \subsection{Trade}\label{subsec:trade}
    These entries in the table below are usually equivalent, local supply and demand may vary them greatly.
    Rolling for price variance might be done if there is no in-world reason why certain things might be more or
    less expensive.
    If that is the case the prices vary by \(((-1)^{1d10}\cdot1d10\cdot5) \%\).
    Additionally everyone a character trades with has self interest and will keep \(5\cdot(11-\)[Negotiation-Check]\()\%\) of
    the tradevalue.\vspace{1.5cm}
    Goods, at 100\% value each line is equivalent to one another and equivalent to 4 character creation points \par
    \subsubsection{Tradegoods}
    \begin{tabular}{|r|l|}
        \hline
        Storage & Article\\\hline
         10g & Elixir of Life (EOL)\\\hline
        100g & Alacast\\\hline
        500g & Experimental Tech Scrap (ETS)\\\hline
        1kg & High Tech Scrap (HTS)\\\hline
        1.5kg & Advanced Gene Therapy Medicine (AGT)\\\hline
        5kg & Medium Tech Scrap (MTS)\\\hline
        10kg & Potent Medicine\\\hline
        50kg & Low Tech Scrap (LTS)\\\hline
        50kg & Seeking Rockets\\\hline
        100kg & Processed Medicine\\\hline
        100kg & Basic Rockets\\\hline
        100kg & Artillery\\\hline
        200kg & Basic Medicine\\\hline
        500kg & Improvised/Herbal Medicine\\hline
        500kg & Base Tech Scrap (BTS)\\\hline
        500kg & Basic Ammunition\\\hline
        1000L & drinking Water (500days of drinking)\\\hline
        500L/35kg & Liquid Hydrogen\\\hline
        1t & Coal\\\hline
        350L & LiquidCombustionFuel\\\hline
        100kg & High Energy Rations (0.4kg/(day\(\cdot\)person))\\\hline
        1t & Normal Food (2.5 kg / (day\(\cdot\)person))\\\hline
        1 & Medium Quality Blueprint\\\hline
    \end{tabular}\par
    Open for more Suggestions\vspace{1.5cm}
    Example:\par
    Character A wants to get rid of 5 tonnes of Base Tech Scrap in favor of more easily transportable Alacast in a local
    Dome.\par
    Since the Gamemaster is lazy there are no storyelements influencing the prices, so they are rolled.
    First, the value of
    the BTS is determined to be (Roll: 6, 4) \(((-1)^{6}\cdot4\cdot5) \% = +20\%\).
    Then the value of Alacast is determined
    to be (Roll: 10, 3)\(((-1)^{10}\cdot3\cdot5) \% = +15\%\).
    The result is that the rate between BTS and Alacast is
    \( 500\cdot1.15/100\cdot1.2 = 4.79\) \\ Which means character As scrap is worth
    \(5000 kg\cdot / 4.79 = 1043 g \) of Alacast.
    He barters (in which he has Proficiency) with a local merchant and manages to
    negotiate terms in which the merchant retains (Roll: 4, 9 \(\Rightarrow\) 9) \(5\cdot(11-9)\% = 10\%\) of the Traded
    value.
    He decides to trade and gets 938 grams of Alacast.\vspace{1.5cm}
    \pagebreak[1]
    \subsection{Combat}\label{subsec:combat}
    \subsubsection{Life}
    Every entity has a pool of Hitpoints, which describes how far away that entity is from its failure point.
    In the case of a Mech, Mount or Human, that would mean being unable to fight or act in an effective manner.
    Living
    entities start dying when they have twice as many wounds as hitpoints.
    How fast something dies is decided by the
    Gamemaster.\par
    If an entity gets damaged, the result of the damage roll (or the number set by the Gamemaster) is compared the results
    of rolls made by the outermost layer of defense.
    If the result of the damage is higher, it, depending on the
    layer of defense, gets blocked, passes through or overwhelms the layer.
    If damage passes all layers of defense,
    it causes damage of a severity of the remaining result.
    Biological Entities for a Biological Entity this is called a wound.
    \subsubsection{Rounds}
    Combat is done in rounds.
    Each round is 5 seconds long.
    Every character present acts in turn (determined
    by circumstances or a Stealth, Perception, Willpower or other situational check) and can usually move and do an action
    (an attack or action that can be done in the remaining time).
    \subsubsection{Combat against Groups}
    The Group is treated as a single Enemy with its pool of Hitpoints being its members.
    It gets offensive/defensive Levels and modifiers assigned by the Gamemaster.\\
    The fighting character decides (if possible, depending on gear and situation) to fight offensively, defensively
    or passively and rolls the respective combat stat, then the differences between each of the rolled dice of the combat
    roll and the groups performance value is calculated.\par
    \begin{enumerate}[label= - ]
        \item Offensive style: For every step of severity in the damage dealt (with an appropriate weapon),
        a Group member is rendered unable to
        fight.
        On Offensive rolls, the group gets a sizebonus correlating to their size and an advantage.
        \item Defensive style: Dealing damage results in a group member being rendered unable to fight.
    \end{enumerate}
    \subsubsection{Detailed combat}
    The attacking character makes their to hit check (dexterity for example).
    The defending character Checks for the
    corresponding defense (agility for example).
    If the attacker wins, they hit, on a draw the
    attack grazes.
    On a hit, check for damage by rolling the damage level of the weapon, subtract the result of the
    armor roll and add difference in sizeclasses between weapon and target.
    If all levels of Defense are breached, the remaining result of the roll is the severity of the inflicted damage.\par
    When sniping, The damage is not inflicted in general, but on a part of the target with a maximum depth equal to
    the severity of the damage.
    For the rest see sniping.
    \subsection{Health and Contamination}\label{subsec:healthAndContamination}
    \subsubsection{Healing}
    For Living entities Damage points are wounds with the severity being the remainder of the result of the damage roll
    after all defenses were subtracted +1 for each other wound.\\
    Humans roll a fitness Check per day and compare it against the severity of each wound, while self healing is
    possible, success lowers the severity of the wound by one step, failure keeps the wounds where they are and
    depending on the wound and environment, a score much (usually 5) lower than the severity infects the wound.\\
    An Infected wound requires a success while selfhealing or treatment to remove the infection, Infecting an already
    infected wound leads to another wound with half the severity (rounded up) of the original being created.
    Infected
    Wounds gain an additional level of  severity each day, starting the day they get infected without an upper limit.
    Treated Wounds not only heal one Level better, they remove the treatment instead of getting infected.
    Permanently
    treated wounds, can not infect. \\
    While a Human has equal to or more wounds than their Lifepool allows for, they are unconscious.
    At Twice that amount
    they die.
    \subsubsection{Treatment}
    Treating of Wounds with a Profession[Medical] Check, where medecine and equipment can get modifiers or Advantages.
    Many Wounds require Medicine to be treated.
    Treating them without will not be possible or generate disadvantage\vspace{1.5cm}
    \begin{tabular}{cl}
        0-x & inflict a point of infected damage of severity 1+x and infect the treated wound\\
        1, 2, 3 & another wound of severity 1\\
        4, 5, 6 & nothing\\
        7, 8, 9 & treat the wound for a day\\
        10 & treat the wound until infection \\
        11 & treat the wound until infection and heal wound by 1 \\
        12 & treat the wound permanently and heal wound by 2 \\
        13 & treat the wound permanently and heal all wounds by 2\\
        13+x & treat all wounds, the treated wound permanently and heal all wounds by 2+x\\
    \end{tabular}\vspace{1.5cm}
    Treating Contamination is not as easy and requires 10g of Alacast.
    Medicine provides no Advantages or Disadvantages
    but equipment and circumstances do.
    In all cases Alacast is used to precipitate Contamination from the body, the
    crudest way is to introduce Alacast to the bloodstream to precipitate it inside the body and hope the body expels
    it on its own, more refined ways are basically a dialysis or a very specific targetting of crystallization seeds
    and retrieval of precipitation clusters via for example highly precise syringes.
    It always lowers Contamination by 1.
    Roll might be Medicine or Red Biotech, depending on circumstances.
        \begin{tabular}{cl}
        0-x & inflict a point of infected damage of severity 5+x \\
        1, 2, 3 & inflict an infected wound of severity 4 \\
        4, 5, 6 & inflict a wound of severity 3\\
        7, 8, 9 & inflict a wound of severity 2\\
        10 & inflict a wound of severity 1\\
        11 & lower Contamination by extra 1 \\
        12 & lower Contamination by extra 2 \\
    \end{tabular}\vspace{1.5cm}
    \subsubsection{Medicine}
    Medicine is used while making a Treatment Check.
    Each Treatment of a wound using Medicine consumes
    severity\(\cdot\)100g of the medicine and provides the specific bonus.
    Improvised or unprocessed Herbal medicine
    requires a check of the related skill first (Herbal/Red Biotech/Blue Biotech and so on) and only works if the check
    has been successfull.
    Herbal Medicine provides a bonus based on the degree of success of the first roll, but if the
    roll fails the Treatment roll is made as if no medicine was present.
    Improvised Medicine always gives the Advantage
    of medicine being present but migt or might not help\\
    Reliable Medicine processed in a modern way does not exhibit variation, though AGT Medicine requires a Red Biotech
    Roll and uses the lower value and the Elixir of Life requires a Black Biotech Roll and contaminates user and patient
    with 10-Result extra Levels of Contamination (even being able to lower Contamination).
    There is no strong
    requirement to make the rolls, not rolling however will result in a result of 0.
    Alacast used as a Medicine does nothing for the Treatment but does provide +1 on the next daily contamination Check
    per full Internal Contamination Level*10g used. (if contamination changes, new value counts).
    \begin{tabular}{cl}
        Medicine & Bonus\\
        Herbal & X\\
        Improvised & 0/1\\
        Basic & 1\\
        Processed & 2\\
        Potent Medicine & 3\\
        AGT Medicine & 5 or X\\
        Elixir of Life & 10 or X\\
    \end{tabular}\vspace{1.5cm}
    \subsubsection{Categories}
    Every Character has a Category ranging from A to C. So called CatA Humans are usually Supervivo, CatBs are outlaws or
    for some reason living outside and CatCs are usually Tribals.
    Every Entity that can be affected by Contamination from buildings over technology to living things have Category ratings.
    The Contaminationresistances of Categories A, B and C are -1, 0 and 1 respectively.\par\vspace{1.5cm}
    \begin{tabular}{c|ccc}
        Entity & Contamination  & (internal) & Intrinsic\\
               & Resistance Level & Resistance Bonus & Contamination\\
        Cat A & 3 & -1 & 0\\
        Cat B & 4 & 0 & 2\\
        Cat C & 5 & 1 & 8\\
        Experimental Tech & 1 & -1 \\
        High Tech & 2 & 0 \\
        Mid Tech & 3 & 1\\
        Low Tech & 4 & 2 \\
        Base Tech & 5 & 3 \\
    \end{tabular}\par\vspace{1.5cm}
    \subsubsection{Contamination}
    Contamination is a term used to describe the amalgamation of technology destroying nanoweapons, radiation, pollution
    and general environmental hazard.
    Contamination is airborne, waterborne, bloodborne and permeates pretty much
    everything in the environment.
    It is usually assigned a level describing its intensity.
    Only within the Domes
    of the Supervivo, inside a Mech or in a similarily purified environment the Contaminationlevel is 0. \\
    Levels below 0 are necessary for taking apart Experimental Tech Technology, but getting an area so pure is hard.\\
    Levels 1--3
    are rare areas of low Contamination, like Mines, Airlocks, outdoor markets, outdoor settlements and so on. \\
    Levels 4--6
    are the most common and usually inhabited by Cat-B\\
    Levels 7--11
    are usually inhabited by tribals but sometimes a few Cat-B have to make Camp here \\
    Levels 12--15
    are sparsely populated by Hardy Tribals, but usually deserted.\\
    Levels 16 and Higher
    are Oceans, Deserts, and other hostile areas.
    Weird Things happen here, but some say there is great treasure\ldots\\
    There is no upper limit for Contaminationlevels. \\*
    If an entity is in an area with Contamination, every hour it receives the local Contamination
    as Contaminationdamage.\par
    \subsubsection{Contaminationdamage}
    Anytime the an Entity receives Contamination damage, the character checks ther Contamination
    Resistance plus all applicable modifiers (external only for external Contamination/internal for both) against the
    level of damage.
    If the Check fails, the entity takes one point of Contamination damage (causing a wound with
    difficulty of the difference between check and Damage and raising Charactercontamination by 1, if applicable).
    If the check fails with a difference of 10 or more, 10 are split off as additional damage. \par
    Charactercontamination is applied as an internal bonus on the Contaminationresistance Check. \par
    Every day before healing a Characters Contamination is applied as damage.
    No Charactercontamination is caused,
    but wounds are taken as normal.
    If the result was a draw or worse, no selfhealing is possible that day.
    Once per hour (about 5 minutes into it) a character directly interacts with an entity, the Charactercontamination*2
    (+Intrinsic Contamination if handling directly) of that character is applied as Contamination damage,
    resisted by a Contaminationresistance of the Entity.
    While directly contacting an entity only the internal
    resistance applies, direct contact might be piloting a mech, using a gun or shaking someones hand, but not being in
    a sealed cargo hold, handling a sealed gun, breathing near someone who wears a face mask, or being processed
    by a decon machine.
    \subsubsection{Seals}
    A seal of a level of X lowers the level of the Contamination behind it by X (they are usually from 6 upwards)
    Contamination still penetrates weak seals.
    Air has to be purified separately or enriched with oxygen.
    (One human consumes about 500--600 litres of oxygen per day.) The Domes of the Supervivo for
    example usually have a level 25 hermetical seal with purified and oxygenenriched air.\vspace{1.5cm}
    Examples of human sized external contamination modifiers or in-place options\vspace{1.5cm}
    \begin{tabular}{cl}
        1& An alacast infused rag or a shut wooden door (although oxygen may run out)\\
        2& a breathermask or a simple wooden door airlock (again, oxygen)\\
        3& a partial gasmask  or an airtight airlock\\
        4& a heavy partial gasmask with Goggles or a basetech air filtering facility\\
        5& a full gasmask\\
        6& as above + sealed clothing or lowtech air filtering facility\\
        7& as above + midtech scrubber (a little backpack)\\
        8& as above + hightech air scrubber or midtech air filtering facility\\
        9& as above + full mask with air from a compressed air tank\\
       10+& specially sealed suit with airtank or hightech filtering facility\\
    \end{tabular}\pagebreak
    \subsubsection{Average Death}
    Average death durations, mortality rate and average ending character contamination
    (with Fitness 3, 0,2,3 starting character contamination respectively and staying in same Contamination
    Level for one month):\par\vspace{0.5cm}
    \begin{tabular*}{20cm}{c @{\extracolsep{\fill}}cccc}
        &Category A & Category B & Category C&
    \end{tabular*}\par
    \fontsize{10}{0}
     \begin{tabular}{c|rlll|rlll|rlll}
C & death & mortality & wounds & con & death & mortality & wounds & con &death & mortality & wounds & con\\
0  &none   	&0    \% &     0 &     0 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
1  &none   	&0    \% &     0 &  0.93 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
2  &398.40 	&0.5  \% &     0 &     2 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
3  &360.86 	&25.2 \% &     1 &     3 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
4  &262.98 	&82.2 \% &     3 &     4 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
5  &145.98 	&99.2 \% &     4 &     5 &none   	&0    \% &     0 &   2.5 &none   	&0    \% &     0 &     3\\
6  & 74.76 	&100  \% &     5 &     6 &none   	&0    \% &     0 &   3.6 &none   	&0    \% &     0 &     3\\
7  & 40.91 	&100  \% &     4 &     7 &302.00 	&1.2  \% &     0 &   4.7 &none   	&0    \% &     0 &     3\\
8  & 24.86 	&100  \% &     4 &   7.6 &314.20 	&14.2 \% &     1 &   5.8 &none   	&0    \% &     0 &   3.3\\
9  & 17.93 	&100  \% &     4 &   7.9 &283.16 	&61   \% &     3 &   6.7 &none   	&0    \% &     0 &   4.2\\
10 & 14.29 	&100  \% &     4 &     8 &195.13 	&92.9 \% &     4 &   7.5 &none   	&0    \% &     0 &   5.3\\
11 & 11.63 	&100  \% &     4 &   7.9 &107.89 	&99.1 \% &     5 &   8.4 &358.00 	&1.2  \% &     0 &   6.4\\
12 &  9.80 	&100  \% &     4 &   7.7 & 65.74 	&100  \% &     6 &   9.3 &265.29 	&13   \% &     1 &   7.4\\
13 &  8.52 	&100  \% &     3 &   7.4 & 47.70 	&100  \% &     6 &    10 &229.25 	&45.1 \% &     2 &   8.2\\
14 &  7.42 	&100  \% &     3 &     7 & 34.66 	&100  \% &     6 &    11 &183.48 	&85.1 \% &     4 &   9.1\\
15 &  6.59 	&100  \% &     3 &   6.5 & 25.85 	&100  \% &     6 &    11 &117.52 	&98.7 \% &     6 &   9.9\\
16 &  6.00 	&100  \% &     3 &     6 & 19.90 	&100  \% &     6 &    12 & 70.58 	&100  \% &     6 &    11\\
17 &  5.54 	&100  \% &     3 &   5.5 & 15.58 	&100  \% &     5 &    12 & 53.38 	&100  \% &     7 &    12\\
18 &  5.21 	&100  \% &     3 &   5.2 & 12.50 	&100  \% &     5 &    12 & 46.93 	&100  \% &     7 &    13\\
19 &  4.84 	&100  \% &     3 &   4.8 & 10.28 	&100  \% &     5 &    11 & 37.97 	&100  \% &     8 &    14\\
20 &  4.56 	&100  \% &     3 &   4.6 &  8.95 	&100  \% &     4 &    11 & 27.45 	&100  \% &     7 &    14\\
21 &  4.28 	&100  \% &     3 &   4.3 &  8.11 	&100  \% &     4 &    10 & 21.14 	&100  \% &     7 &    14\\
22 &  4.09 	&100  \% &     3 &   4.1 &  7.32 	&100  \% &     4 &   9.3 & 16.15 	&100  \% &     6 &    14\\
23 &  4.00 	&100  \% &     3 &     4 &  6.59 	&100  \% &     4 &   8.6 & 12.41 	&100  \% &     6 &    14\\
24 &  4.00 	&100  \% &     3 &     4 &  5.97 	&100  \% &     4 &     8 & 10.36 	&100  \% &     6 &    13\\
25 &  4.00 	&100  \% &     3 &     4 &  5.54 	&100  \% &     4 &   7.5 &  9.18 	&100  \% &     6 &    12\\
26 &  4.00 	&100  \% &     3 &     4 &  5.20 	&100  \% &     4 &   7.2 &  8.24 	&100  \% &     6 &    11\\
27 &  4.00 	&100  \% &     3 &     4 &  5.01 	&100  \% &     4 &     7 &  7.42 	&100  \% &     5 &    10\\
28 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.79 	&100  \% &     5 &   9.8\\
29 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.32 	&100  \% &     5 &   9.3\\
30 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.04 	&100  \% &     5 &     9\\
31 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.00 	&100  \% &     5 &     9\\
        \end{tabular}\par
    \subsection{Tech}\label{subsec:tech}
    Electrolysis splits 1 L H2O into 622.22 L Oxygen und 1244.4 using 3.7037 kwh\\
    \subsubsection{Blueprints}
(rework on its way)
    Blueprints are required for building(engineering) tasks.
    To create a blueprint a character needs the appropriate materials
    (usually a computer of some sort) the time required is based on the complexity of the project.
    To find out if the
    blueprint is within the capAttributes of the character check their specific Knowledge against the difficulty of the
    project.
    If the Character does not have the Appropriate Knowledge he can check sufficiently similar knowledge with
    an appropriate disadvantage (1 per techlevel, 3 for different module classes on the same techlevel)
    The modifier the blueprint provides is the result of the Check\(/2\)(rounded up)\(-3\).
    Even a blueprint with a negative bonus is useful, since it enables the Attribute to build the item in question at all.\\
    A blueprint states the name of the Item, its category and the required materials.\vspace{1.5cm}
    \subsubsection{Engineering}
(rework on its way)
    Building something requires a blueprint, the required materials, a workshop or something similar.
    Check Engineering
    modified by the blueprint bonus and the conditions (having nothing but a makeshift wrench in the desert might be -5, having state of the art
    tools in an antigravpowered workshop might be +3).
    The finished product is [check result \(\cdot\) 10\%] Efficient.
    (for example damage per round, Coverage, poweroutput and so on)\vspace{1.5cm}