\documentclass{article}
\usepackage{geometry}
\usepackage{listings}
\usepackage{layout}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{dirtree}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\geometry{textheight=25cm, hoffset=0cm, textwidth = 19cm}
\title{Endworld PnP}
\author{Maric}
\date{}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\begin{document}
    \maketitle
    \tableofcontents
    \section{The EndWorld}

    Years have gone by since the Great War. Many Years. Even though few remember how long it has been, the remnants
    of a time long gone still remind us that once, long ago, the world has been a nicer place. But, the world we know
    now ... is not a nice place. Such a shame. I have lived a long life, and I have learned to adapt to the new World,
    but just as the Contamination eats away at technology and the lives of those who come into contact with it, time
    eats away at me. Such a shame, there is so little of it left for me. But the plans are in motion, Immortality might
    be in my grasp.\par
    I am ... well, it seems some Details are starting to slip my mind. I am Quaesitor, and yet again I am wrong, but
    not entirely. I was Quaesitor. I traveled from the great city of Terracina to the quaint outpost of Kodal to
    learn. A life time of learning of trying to protect what the Supervivo have protected so long. The ancient Knowledge
    and ancient Arts. Microelectronics. Quantum Physics. The like. We, the Survivors, the Triumphant, the Conquerors,
    forced to huddle in what were mere shelters for what would be a storm that has not blown over in centuries, it is such
    a shame. Marvels of modern Technology have kept me from dying these past 240 years since i retired, but no army of
    hightech mechs, no experimental biotech treatment seems to be able to extend my mind. I have forgotten so much.
    \par Such a shame.\par
    Of course we are not the only ones who survived. Beasts stalk the Lands, ferocious beasts, Megafauna, sly, intelligent
    and hungry creatures. In some cases literally. But even Humanoids, a pale imitation of real Humans, the descendants
    of vile mutants, vile mutants and savages themselves, such a shame to human kind. They raid caravans, keep to their
    barbaric cultures, forever cursed to Harbor the very Contamination killing their chances of ever knowing the pleasures
    of technology. And it seems that they have interfaced with and adapted to the Contamination, so it doesnt even kill
    them. Such a shame. \par
    Alacast can purify them just like anyone else, it changes the supernatural Contamination back to more normal
    Contamination, that is even mostly harmless to not just the Tribals but real Humans as well. Tribals can live without
    the Contamination, if ever someone would invest in cleaning a Savage up that much, they still can not contribute.
    I have tried. Some babble about cages and insults, barely comprehensible ramblings in their animalistic mockery of
    speech. They do not usually last long once they have gone through decon. Especially those infuriating Individuals
    who seem to have allied with the Contamination trying to kill us all, wielding its Zones Of Normalcy Exclusion like
    weapons. Such a shame. Wide ZONEs of heightened gravity or brittleness, Oxygen free ZONEs or pure Oxydation. Such a
    shame that they have to appear at all even if caused by natural sources. Savages funneling Contamination into a ZONE
    until even the best seal breaks down and the Pilots are eaten alive... Such a Shame.\newline
    \newline
    - Transcript of the only Conversation the oldest Document in the Great Library of Kodal - a severely damaged
    upload of the Brain of an ancient Scientist - will have.\newpage

    \section{Rules}
    \subsection{Rolling and Checks}

    This System uses 3 ten sided dice. A Check is a roll of one to three D10, interpreted
    in a certain way, with the result describing how successfull on a scale of 1-10 the attempted action was.
    1-4 are usually bad, 5 is usually neutral and above that are usually degrees of success.
    This may change depending on situation. \par
    The number of dice rolled and the way they are interpeted varies with Advantage.
    Circumstances that are favourable for the action may give Advantage, while circumstances
    that are unfavourable may subtract from that Advantage (give Disadvantage).
    Minor factors are usually expressed in a change of the required result of the check. Under certain circumstances (like
    good roleplay or similar) the Gamemaster may grant reroll, which allows the player to choose one die of the Check after
    it has been rolled and reroll it. The new result counts instead of the old one. \newline\newline
    How many dice are rolled for a Check and how they are interpreted can be found in the table:\par
    \subsubsection{Dice}
    \begin{tabular}{c|c|c|l}
        Advantage & Level & Dice & Interpretation \\
        -2& 1& 3& take lowest\\
        \hline
        -1& 2& 2& take lowest\\
        \hline
        +0& 3& 1&\\
        \hline
        +1& 4& 2& take highest\\
        \hline
        +2& 5& 3& take highest\\
    \end{tabular}\\
    \vspace{2cm}\\
    When two dice show the same result, they are "added" to go one further into the direction of the current roll.\\
    When three dice show the same result, they are "added" to go two instead.\\
    Examples: \par
    Level 5 Roll: (2,5,5) => 6 \par
    Advantage -2 Roll (9,9,9) => 7 \par
    Level 4 Roll (10,10) => 11 \par

    \subsection{Skills and Abilities}
    Abilities represent in what aspects of the gameworld a character excels and in which he doesnt.

    With the Exception of Knowledges and Professions every Ability starts at Level 1. \par
    Depending on the Priorities picked during character creation it may be easier or harder to raise them, but Every
    Ability can be Applied to a multitude of general Actions. For example Negotiation can be used while bartering or trying
    to convince someone not to harm a hostage. The Priorities and Abilities in the following Table are a not all that exist
    but they are the most common Abilities shared by all humans.\newline\newline

    \begin{tabular}{l||cccccc}
        Priorities       &Social       &Mental         &Physical      \\\hline\\
                        &Negotiation  &Perception     &Fitness        \\
        Abilities       &Expression   &Mind           &Dexterity      \\
                        &Slyness      &Resonance      &Agility        \\
    \end{tabular}\newline

    \subsubsection{Social Abilities} 
        \begin{enumerate}[label= -]
            \item {Negotiation}: employing discussion, bartering, negotiating and similar interactions.
            \item {Expression}: Leadership, telling a story, reporting, and building rapport.
            \item {Slyness}: lying, skullduggery, twisting the truth and intimidation.
        \end{enumerate}
    \subsubsection{Mental Abilities} 
        \begin{enumerate}[label=-]
            \item {Perception}: How well information is gathered from the world.
            \item {Mind}: Memory, assessing situations, processing information.
            \item {Resonance}: the marginal edge that goes beyond the normal and expected, this barely understood trait
            describes the brains ability to ... connect.
        \end{enumerate}
    \subsubsection{Physical Abilities} 
        \begin{enumerate}[label= -]
            \item {Fitness}: General physical shape, Strength, Stamina, Healing.
            \item {Dexterity}: Precise physical manipulations of all sorts.
            \item {Agility}: Speed, Acrobatics, maneuverability.
        \end{enumerate}
    \subsubsection{Tech Abilities}
        \begin{enumerate}[label= -]
            \item {Usage}: How to handle and operate complicated (or unknown) technology.
            \item {Analysis}: Gathering information about the workings and purposes of complicated or unknown technology
            \item {Integration}: Wiring/interfacing technology together that might or might not have been build for
            that purpose.
        \end{enumerate}
        \subsubsection{Weapons Expertise}
        \paragraph{Laser}s or technically "Directed Energy Weapons" \newline are a group of weapons which typically
    do not use Ammunition, but raw Energy to inflict their damage. Their comparably low damage is made up for by being
    as accurate as a light beam. Plus the high amounts of particles in the air make for pretty lights.
        \begin{enumerate}[label= -]
            \item {Pulse} Weapons that emit short, sometimes repeated pulses of energy, mostly to save on heat, but also
            to be able to use special capacitors to deliver powerful bursts of energy.
            \item {Beam} Weapons that emit long, sometimes even sustained streams of energy, making them easier to aim
            and inflicting more damage, usually at the price of higher sustained energy and heat costs.
        \end{enumerate}
        \paragraph{Projectile} Weapons or sometimes just "Guns" \newline are a group of weapons which discharge Projectiles
        towards a target. Ammunition has to be employed, but there are several different types available.
        \begin{enumerate}[label= -]
            \item{Direct} Projectile Weapons are many and varied but share the characteristic of being pointed roughly at
            the target they are shooting. They require line of sight.
            \item{Indirect} Projectile Weapons are just as varied as Direct Projectile Weapons but have the key difference
            of not pointing at the target. Usually Up in an angle. They require information about the targets position,
            but are free from line of sight restrictions the Projectile still has to have a valid way to travel to be used.
        \end{enumerate}
        \paragraph{Biotech} is the Fusion of Biology and Technology \newline The ancient texts define Biotechnology as
        "any technological application that uses biological systems, living organisms, or derivatives thereof, to make
        or modify products or processes for specific use".
        \begin{enumerate}[label= -]
            \item{Red} Biotechnology Encompasses genetics, genomics, pharmacology, but also medical advances like
            genetherapy and automedics and deconamination of living things.
            \item{Green} Biotechnology is used every time the passive environment is exploited, from high yield,
            low footprint farming to harnessing the great and small Anomalies, including detoxification of materials and
            Beings.
            \item{Blue} Biotechnology has developed from being used for aquatic Biotech, to include Megafauna, since the
            first Megafauna is told to having been spottet in the ocean. It allows scanning, categorization and
            assessment of Megafauna, including in some cases, harvesting Megafauna specialities.
            \item{White} or Industrial. It is used in Industrial processes and in handling some of the results of such
            processes. Creating and/or applying contamination-sealant is one of such processes.
            \item{Black} deals with with integration of Biology and Technology from enhancements or replacements like
            Cyberware or more conventional Prosthetics to synthesizing life, ressurection and strong AI. Seldomly useful
            and the most dangerous brand of Biotechnology, it is not taught often.
        \end{enumerate}
    \pagebreak
    \subsubsection{Skilltree - Techside}
    Further Priorities might include Abilities, single Skills or Entire Skilltrees. A number in brackets indicates how many
    Skillpoints can be assigned, lacking a number implies being either a category (nodes) or an ability (leaves).
    \dirtree{%
    .1 Skills.
    .2 Tech Abilities.
    .3 Usage.
    .3 Analysis.
    .3 Integration.
    .2 Mech Skills.
    .3 Weapons Expertise.
    .4 Laser.
    .5 Pulse.
    .5 Beam.
    .4 Projectile.
    .5 Direct.
    .5 Indirect.
    .4 Missiles.
    .5 Seeking.
    .5 Dumbfire.
    .4 Melee.
    .5 Sharp.
    .5 Blunt.
    .5 Unarmed.
    .3 Piloting Practice.
    .4 Exo.
    .4 Tiny.
    .4 Very Light.
    .4 Light.
    .4 Medium.
    .4 Heavy.
    .4 Very Heavy.
    .4 Ultra.
    .3 Auxilliary Training.
    .4 Defense.
    .5 Decoys.
    .5 Shields.
    .5 Deflectors.
    .4 Offense.
    .5 Explosives.
    .5 Sniping.
    .5 Speciality Gadgets.
    .4 Recon.
    .5 Scanners.
    .5 Suppressors.
    .5 Sabotage.
    .4 Utility.
    .5 Communications.
    .5 Reprocessing.
    .5 Utility Movement.
    .4 Biotech.
    .5 Red.
    .5 Green.
    .5 Blue.
    .5 White.
    .5 Black.
    }
    \pagebreak
    \subsection{Trade}

    These entries in the table below are usually equivalent, local supply and demand may vary them greatly.
    Rolling for price variance might be done if there is no in-world reason why certain things might be more or
    less expensive. If that is the case the prices vary by \(((-1)^{1d10}\cdot1d10\cdot5) \%\).
    Additionally everyone a character trades with has self interest and will keep \(5\cdot(11-\)[Negotiation-Check]\()\%\) of
    the tradevalue.\newline \newline
    Goods, at 100\% value each line is equivalent to one another and equivalent to 4 character creation points \par
    \subsubsection{Tradegoods}
    \begin{tabular}{|r|l|}
        \hline
        Storage & Article\\\hline
         10g & Elixir of Life (EOL)\\\hline
        100g & Alacast\\\hline
        500g & Experimental Tech Scrap (ETS)\\\hline
        1kg & High Tech Scrap (HTS)\\\hline
        1.5kg & Advanced Gene Therapy Medicine (AGT)\\\hline
        5kg & Medium Tech Scrap (MTS)\\\hline
        10kg & Potent Medicine\\\hline
        50kg & Low Tech Scrap (LTS)\\\hline
        50kg & Seeking Rockets\\\hline
        100kg & Processed Medicine\\\hline
        100kg & Basic Rockets\\\hline
        100kg & Artillery\\\hline
        200kg & Basic Medicine\\\hline
        500kg & Improvised/Herbal Medicine\\hline
        500kg & Base Tech Scrap (BTS)\\\hline
        500kg & Basic Ammunition\\\hline
        1000L & drinking Water (500days of drinking)\\\hline
        500L/35kg & Liquid Hydrogen\\\hline
        1t & Coal\\\hline
        350L & LiquidCombustionFuel\\\hline
        100kg & High Energy Rations (0.4kg/(day\(\cdot\)person))\\\hline
        1t & Normal Food (2.5 kg / (day\(\cdot\)person))\\\hline
        1 & Medium Quality Blueprint\\\hline

    \end{tabular}\par
    Open for more Suggestions\newline
    \newline
    Example:\par
    Character A wants to get rid of 5 tonnes of Base Tech Scrap in favor of more easily transportable Alacast in a local
    Dome.\par
    Since the Gamemaster is lazy there are no storyelements influencing the prices, so they are rolled. First, the value of
    the BTS is determined to be (Roll: 6, 4) \(((-1)^{6}\cdot4\cdot5) \% = +20\%\). Then the value of Alacast is determined
    to be (Roll: 10, 3)\(((-1)^{10}\cdot3\cdot5) \% = +15\%\). The result is that the rate between BTS and Alacast is
    \( 500\cdot1.15/100\cdot1.2 = 4.79\) \\ Which means character As scrap is worth
    \(5000 kg\cdot / 4.79 = 1043 g \) of Alacast. He barters (in which he has Proficiency) with a local merchant and manages to
    negotiate terms in which the merchant retains (Roll: 4, 9 \(\Rightarrow\) 9) \(5\cdot(11-9)\% = 10\%\) of the Traded
    value. He decides to trade and gets 938 grams of Alacast.\newline\newline
    \pagebreak[1]
    \subsection{Combat}

    \subsubsection{Life}
    Every entity has a pool of Hitpoints, which describes how far away that entity is from its failure point.
    In the case of a Mech, Mount or Human, that would mean being unable to fight or act in an effective manner. Living
    entities start dying when they have twice as many wounds as hitpoints. How fast something dies is decided by the
    Gamemaster.\par
    If an entity gets damaged, the result of the damage roll (or the number set by the Gamemaster) is compared the results
    of rolls made by the outermost layer of defense. If the result of the damage is higher, it, depending on the
    layer of defense, gets blocked, passes through or overwhelms the layer. If damage passes all layers of defense,
    it causes damage of a severity of the remaining result.
    Biological Entities for a Biological Entity this is called a wound.

    \subsubsection{Rounds}
    Combat is done in rounds. Each round is 5 seconds long. Every character present acts in turn (determined
    by circumstances or a Stealth, Perception, Willpower or other situational check) and can usually move and do an action
    (an attack or action that can be done in the remaining time).

    \subsubsection{Combat against Groups}
    The Group is treated as a single Enemy with its pool of Hitpoints being its members.
    It gets offensive/defensive Levels and modifiers assigned by the Gamemaster.\\

    The fighting character decides (if possible, depending on gear and situation) to fight offensively, defensively
    or passively and rolls the respective combat stat, then the differences between each of the rolled dice of the combat
    roll and the groups performance value is calculated.\par
    \begin{enumerate}[label= - ]

        \item Offensive style: For every step of severity in the damage dealt (with an appropriate weapon),
        a Group member is rendered unable to
        fight. On Offensive rolls, the group gets a sizebonus correlating to their size and an advantage.\\

        \item Defensive style: Dealing damage results in a group member being rendered unable to fight.\\
    \end{enumerate}

    \subsubsection{Detailed combat}
    The attacking character makes their to hit check (dexterity for example). The defending character Checks for the
    corresponding defense (agility for example). If the attacker wins, they hit, on a draw the
    attack grazes. On a hit, check for damage by rolling the damage level of the weapon, subtract the result of the
    armor roll and add difference in sizeclasses between weapon and target.
    If all levels of Defense are breached, the remaining result of the roll is the severity of the inflicted damage.\newline
    When sniping, The damage is not inflicted in general, but on a part of the target with a maximum depth equal to
    the severity of the damage. For the rest see sniping.

    \subsection{Health and Contamination}

    \subsubsection{Healing}
    For Living entities Damage points are wounds with the severity being the remainder of the result of the damage roll
    after all defenses were subtracted +1 for each other wound.\\
    Humans roll a fitness Check per day and compare it against the severity of each wound, while self healing is
    possible, success lowers the severity of the wound by one step, failure keeps the wounds where they are and
    depending on the wound and environment, a score much (usually 5) lower than the severity infects the wound.\\
    An Infected wound requires a success while selfhealing or treatment to remove the infection, Infecting an already
    infected wound leads to another wound with half the severity (rounded up) of the original being created. Infected
    Wounds gain an additional level of  severity each day, starting the day they get infected without an upper limit.
    Treated Wounds not only heal one Level better, they remove the treatment instead of getting infected. Permanently
    treated wounds, can not infect. \\
    While a Human has equal to or more wounds than their Lifepool allows for, they are unconscious. At Twice that amount
    they die.
    \subsubsection{Treatment}
    Treating of Wounds with a Profession[Medical] Check, where medecine and equipment can get modifiers or Advantages.
    Many Wounds require Medicine to be treated. Treating them without will not be possible or generate disadvantage\\\\
    \begin{tabular}{cl}
        0-x & inflict a point of infected damage of severity 1+x and infect the treated wound\\
        1, 2, 3 & another wound of severity 1\\
        4, 5, 6 & nothing\\
        7, 8, 9 & treat the wound for a day\\
        10 & treat the wound until infection \\
        11 & treat the wound until infection and heal wound by 1 \\
        12 & treat the wound permanently and heal wound by 2 \\
        13 & treat the wound permanently and heal all wounds by 2\\
        13+x & treat all wounds, the treated wound permanently and heal all wounds by 2+x\\
    \end{tabular}\\\\
    Treating Contamination is not as easy and requires 10g of Alacast. Medicine provides no Advantages or Disadvantages
    but equipment and circumstances do. In all cases Alacast is used to precipitate Contamination from the body, the
    crudest way is to introduce Alacast to the bloodstream to precipitate it inside the body and hope the body expels
    it on its own, more refined ways are basically a dialysis or a very specific targetting of crystallization seeds
    and retrieval of precipitation clusters via for example highly precise syringes. It always lowers Contamination by 1.
    Roll might be Medicine or Red Biotech, depending on circumstances.
        \begin{tabular}{cl}
        0-x & inflict a point of infected damage of severity 5+x \\
        1, 2, 3 & inflict an infected wound of severity 4 \\
        4, 5, 6 & inflict a wound of severity 3\\
        7, 8, 9 & inflict a wound of severity 2\\
        10 & inflict a wound of severity 1\\
        11 & lower Contamination by extra 1 \\
        12 & lower Contamination by extra 2 \\
    \end{tabular}\\\\

    \subsubsection{Medicine}
    Medicine is used while making a Treatment Check. Each Treatment of a wound using Medicine consumes
    severity\(\cdot\)100g of the medicine and provides the specific bonus. Improvised or unprocessed Herbal medicine
    requires a check of the related skill first (Herbal/Red Biotech/Blue Biotech and so on) and only works if the check
    has been successfull. Herbal Medicine provides a bonus based on the degree of success of the first roll, but if the
    roll fails the Treatment roll is made as if no medicine was present. Improvised Medicine always gives the Advantage
    of medicine being present but migt or might not help\\
    Reliable Medicine processed in a modern way does not exhibit variation, though AGT Medicine requires a Red Biotech
    Roll and uses the lower value and the Elixir of Life requires a Black Biotech Roll and contaminates user and patient
    with 10-Result extra Levels of Contamination (even being able to lower Contamination). There is no strong
    requirement to make the rolls, not rolling however will result in a result of 0.
    Alacast used as a Medicine does nothing for the Treatment but does provide +1 on the next daily contamination Check
    per full Internal Contamination Level*10g used. (if contamination changes, new value counts).
    \begin{tabular}{cl}
        Medicine & Bonus\\
        Herbal & X\\
        Improvised & 0/1\\
        Basic & 1\\
        Processed & 2\\
        Potent Medicine & 3\\
        AGT Medicine & 5 or X\\
        Elixir of Life & 10 or X\\
    \end{tabular}\\\\*

    \subsubsection{Categories}
    Every Character has a Category ranging from A to C. So called CatA Humans are usually Supervivo, CatBs are outlaws or
    for some reason living outside and CatCs are usually Tribals.
    Every Entity that can be affected by Contamination from buildings over technology to living things have Category ratings.
    The Contaminationresitances of Categories A, B and C are -1, 0 and 1 respectively.\\\newline
    \begin{tabular}{c|ccc}
        Entity & Contamination Resistance Level & (internal) Resistance Bonus & Intrinsic Contamination\\
        Cat A & 3 & -1 & 0\\
        Cat B & 4 & 0 & 2\\
        Cat C & 5 & 1 & 8\\
        Experimental Tech & 1 & -1 \\
        High Tech & 2 & 0 \\
        Mid Tech & 3 & 1\\
        Low Tech & 4 & 2 \\
        Base Tech & 5 & 3 \\
    \end{tabular}\newline\newline

    \subsubsection{Contamination}
    Contamination is a term used to describe the amalgamation of technology destroying nanoweapons, radiation, pollution
    and general environmental hazard. Contamination is airborne, waterborne, bloodborne and permeates pretty much
    everything in the environment. It is usually assigned a level describing its intensity. Only within the Domes
    of the Supervivo, inside a Mech or in a similarily purified environment the Contaminationlevel is 0. \\
    Levels below 0 are necessary for taking apart Experimental Tech Technology, but getting an area so pure is hard.\\
    Levels 1-3
    are rare areas of low Contamination, like Mines, Airlocks, outdoor markets, outdoor settlements and so on. \\
    Levels 4-6
    are the most common and usually inhabited by Cat-B\\
    Levels 7-11
    are usually inhabited by tribals but sometimes a few Cat-B have to make Camp here \\
    Levels 12-15
    are sparsely populated by Hardy Tribals, but usually deserted.\\
    Levels 16 and Higher
    are Oceans, Deserts, and other hostile areas. Weird Things happen here, but some say there is great treasure...\\
    There is no upper limit for Contaminationlevels. \\*

    If an entity is in an area with Contamination, every hour it receives the local Contamination
    as Contaminationdamage.\par

    \subsubsection{Contaminationdamage}
    Anytime the an Entity receives Contamination damage, the character checks ther Contamination
    Resistance plus all applicable modifiers (external only for external Contamination/internal for both) against the
    level of damage. If the Check fails, the entity takes one point of Contamination damage (causing a wound with
    difficulty of the difference between check and Damage and raising Charactercontamination by 1, if applicable).
    If the check fails with a difference of 10 or more, 10 are split off as additional damage. \\
    Charactercontamination is applied as an internal bonus on the Contaminationresistance Check. \\

    Every day before healing a Characters Contamination is applied as damage. No Charactercontamination is caused,
    but wounds are taken as normal. If the result was a draw or worse, no selfhealing is possible that day.
    Once per hour (about 5 minutes into it) a character directly interacts with an entity, the Charactercontamination*2
    (+Intrinsic Contamination if handling directly) of that character is applied as Contamination damage,
    resisted by a Contaminationresistance of the Entity. While directly contacting an entity only the internal
    resistance applies, direct contact might be piloting a mech, using a gun or shaking someones hand, but not being in
    a sealed cargo hold, handling a sealed gun, breathing near someone who wears a face mask, or being processed
    by a decon machine. \\

    \subsubsection{Seals}
    A seal of a level of X lowers the level of the Contamination behind it by X (they are usually from 6 upwards)
    Contamination still penetrates weak seals. Air has to be purified separately or enriched with oxygen.
    (One human consumes about 500-600 litres of oxygen per day.) The Domes of the Supervivo for
    example usually have a level 25 hermetical seal with purified and oxygenenriched air.\\\\*
    Examples of human sized external contamination modifiers or in-place options\\\\
    \begin{tabular}{cl}
        1& An alacast infused rag or a shut wooden door (although oxygen may run out)\\
        2& a breathermask or a simple wooden door airlock (again, oxygen)\\
        3& a partial gasmask  or an airtight airlock\\
        4& a heavy partial gasmask with Goggles or a basetech air filtering facility\\
        5& a full gasmask\\
        6& as above + sealed clothing or lowtech air filtering facility\\
        7& as above + midtech scrubber (a little backpack)\\
        8& as above + hightech air scrubber or midtech air filtering facility\\
        9& as above + full mask with air from a compressed air tank\\
       10+& specially sealed suit with airtank or hightech filtering facility\\
    \end{tabular}\\\pagebreak\\

    \subsubsection{Average Death}
    Average death durations, mortality rate and average ending character contamination
    (with Fitness 3, 0,2,3 starting characon respectively and staying in same Contaminaion Level for one month):\\\\

    \begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}lcrc}
        &Category A & Category B & Category C&\\
    \end{tabular*}\\
     \begin{tabular}{c|rlll|rlll|rlll}
C & death & mortality & wounds & con & death & mortality & wounds & con &death & mortality & wounds & con\\
0  &none   	&0    \% &     0 &     0 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
1  &none   	&0    \% &     0 &  0.93 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
2  &398.40 	&0.5  \% &     0 &     2 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
3  &360.86 	&25.2 \% &     1 &     3 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
4  &262.98 	&82.2 \% &     3 &     4 &none   	&0    \% &     0 &     2 &none   	&0    \% &     0 &     3\\
5  &145.98 	&99.2 \% &     4 &     5 &none   	&0    \% &     0 &   2.5 &none   	&0    \% &     0 &     3\\
6  & 74.76 	&100  \% &     5 &     6 &none   	&0    \% &     0 &   3.6 &none   	&0    \% &     0 &     3\\
7  & 40.91 	&100  \% &     4 &     7 &302.00 	&1.2  \% &     0 &   4.7 &none   	&0    \% &     0 &     3\\
8  & 24.86 	&100  \% &     4 &   7.6 &314.20 	&14.2 \% &     1 &   5.8 &none   	&0    \% &     0 &   3.3\\
9  & 17.93 	&100  \% &     4 &   7.9 &283.16 	&61   \% &     3 &   6.7 &none   	&0    \% &     0 &   4.2\\
10 & 14.29 	&100  \% &     4 &     8 &195.13 	&92.9 \% &     4 &   7.5 &none   	&0    \% &     0 &   5.3\\
11 & 11.63 	&100  \% &     4 &   7.9 &107.89 	&99.1 \% &     5 &   8.4 &358.00 	&1.2  \% &     0 &   6.4\\
12 &  9.80 	&100  \% &     4 &   7.7 & 65.74 	&100  \% &     6 &   9.3 &265.29 	&13   \% &     1 &   7.4\\
13 &  8.52 	&100  \% &     3 &   7.4 & 47.70 	&100  \% &     6 &    10 &229.25 	&45.1 \% &     2 &   8.2\\
14 &  7.42 	&100  \% &     3 &     7 & 34.66 	&100  \% &     6 &    11 &183.48 	&85.1 \% &     4 &   9.1\\
15 &  6.59 	&100  \% &     3 &   6.5 & 25.85 	&100  \% &     6 &    11 &117.52 	&98.7 \% &     6 &   9.9\\
16 &  6.00 	&100  \% &     3 &     6 & 19.90 	&100  \% &     6 &    12 & 70.58 	&100  \% &     6 &    11\\
17 &  5.54 	&100  \% &     3 &   5.5 & 15.58 	&100  \% &     5 &    12 & 53.38 	&100  \% &     7 &    12\\
18 &  5.21 	&100  \% &     3 &   5.2 & 12.50 	&100  \% &     5 &    12 & 46.93 	&100  \% &     7 &    13\\
19 &  4.84 	&100  \% &     3 &   4.8 & 10.28 	&100  \% &     5 &    11 & 37.97 	&100  \% &     8 &    14\\
20 &  4.56 	&100  \% &     3 &   4.6 &  8.95 	&100  \% &     4 &    11 & 27.45 	&100  \% &     7 &    14\\
21 &  4.28 	&100  \% &     3 &   4.3 &  8.11 	&100  \% &     4 &    10 & 21.14 	&100  \% &     7 &    14\\
22 &  4.09 	&100  \% &     3 &   4.1 &  7.32 	&100  \% &     4 &   9.3 & 16.15 	&100  \% &     6 &    14\\
23 &  4.00 	&100  \% &     3 &     4 &  6.59 	&100  \% &     4 &   8.6 & 12.41 	&100  \% &     6 &    14\\
24 &  4.00 	&100  \% &     3 &     4 &  5.97 	&100  \% &     4 &     8 & 10.36 	&100  \% &     6 &    13\\
25 &  4.00 	&100  \% &     3 &     4 &  5.54 	&100  \% &     4 &   7.5 &  9.18 	&100  \% &     6 &    12\\
26 &  4.00 	&100  \% &     3 &     4 &  5.20 	&100  \% &     4 &   7.2 &  8.24 	&100  \% &     6 &    11\\
27 &  4.00 	&100  \% &     3 &     4 &  5.01 	&100  \% &     4 &     7 &  7.42 	&100  \% &     5 &    10\\
28 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.79 	&100  \% &     5 &   9.8\\
29 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.32 	&100  \% &     5 &   9.3\\
30 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.04 	&100  \% &     5 &     9\\
31 &  4.00 	&100  \% &     3 &     4 &  5.00 	&100  \% &     4 &     7 &  6.00 	&100  \% &     5 &     9\\
        \end{tabular}\\


    \subsection{Tech}
    Electrolysis splits 1 L H2O into 622.22 L Oxygen und 1244.4 using 3.7037 kwh\\
    \subsubsection{Blueprints}
(rework on its way)
    Blueprints are required for building(engineering) tasks. To create a blueprint a character needs the appropriate materials
    (usually a computer of some sort) the time required is based on the complexity of the project. To find out if the
    blueprint is within the capabilities of the character check their specific Knowledge against the difficulty of the
    project. If the Character does not have the Appropriate Knowledge he can check sufficiently similar knowledge with
    an appropriate disadvantage (1 per techlevel, 3 for different module classes on the same techlevel)
    The modifier the blueprint provides is the result of the Check\(/2\)(rounded up)\(-3\).
    Even a blueprint with a negative bonus is useful, since it enables the ability to build the item in question at all.\\
    A blueprint states the name of the Item, its category and the required materials.\\\\

    \subsubsection{Engineering}
(rework on its way)
    Building something requires a blueprint, the required materials, a workshop or something similar. Check Engineering
    modified by the blueprint bonus and the conditions (having nothing but a makeshift wrench in the desert might be -5, having state of the art
    tools in an antigravpowered workshop might be +3). The finished product is [check result \(\cdot\) 10\%] Efficient.
    (for example damage per round, Coverage, poweroutput and so on)\\\\


    \section{Character Creation}
    [rework mostly done]
    First, get a general idea who your character is and what they do. Note your Character name, your name, the name of the
    Campaign and your concept for the character on the Sheet. This will help you choose in the following steps.

    \subsection{Step 1 - Categories}

    Choose Category:\\\\
    If you have grown up without being in contact with Contamination you are probably a Dome dwelling Category A Supervivo. \\
    \begin{tabular}{c|l}
        & low hp (4)\\
        & barely any contamination resistance\\
        Category A     & no tech restrictions\\
        & social/educated skills more likely\\
        & DNI possible\\\hline
        & medium hp (5)\\
        & slightly contamination resistant\\
        Category B    & experimental and high tech tend to degrade fast\\
        & practical/combat skills more likely\\
        & able to pilot and survive outside\\\hline
        & high HP (6) \\
        & highly contamination resistant \\
        Category C & anything above basetech, degrades fast\\
        & survival/physical skills more likely\\
        & controlling contamination possible
    \end{tabular}\newline


    \par

    Note your Category and Lifepoint maximum on your Sheet. You may choose your starting Contamination from 0-5 at no cost and note
    it as well. (although you will start dying if it is too much, read up on Charactercontamination in the chapter Contamination)\\

    \subsection{Step 2 - Abilities}
    Prioritize Social, Physical, Mental, Experience and Training in the order that you think they are most
    usefull to your character concept in. \newline
    In your primary priority you get 25 points, in your secondary priority you get 20 points and in your tertiary
    priority you get 15 points. The remaining Two Priorities get 10 points.\newline
    Within Social, Physical and Mental you can spend your new rating in points to raise an ability by 1, You start with 1
    in Everything. Raising Fitness From one to 4 would cost 2+3+4 = 9 points.\newline
    With Experience You can Pick a Profession, for example Engineer, Medic, Scientist, or a Knowledge for Example
    Geology, Local History Italy, Quantum Mechanics, High Tech Shields, and Note them on Your Character Sheet. They start at
    0. Professions are Abilities, Knowledges are Skills and cost one point per Level. (Knowledges need to be narrow enough,
    Knowledge about Technology needs to be specified to Category of Technology and Techlevel. Related Knowledges might give
    a lesser advantage.)\\

    In the Training Category you can apply your points to the Tech Abilities or the skills from the Skilltree.
    Every Skill is capped at the level of the node above it. If a Characters Weapon Level is 3, the Characters Projectile
    Level can not exceed 3. The Skill Direct(Projectile Weapons) itself, in turn can not exceed the Projectile Level.\\


    Unspent Points remain. Every point requires some sort of mention in the Backstory of the Character, more than 3 points
    in something require a good reason which intertwines with the story of the Character.

    Later Points are awarded to the categories depending on roleplay and successfull missions or can be bought from
    trainers. All such points need to have an ingame reason. Knowledges can only be learned through teachers, sources or
    years of study, a new Training either needs a Teacher or a long time\\


    \subsection{Step 3 - Finishing touches}
    You get 80 Credits, you can spend these on:
    Your Mech (see below)\\
    Goods 1:4 (see table in chapter Trade)\\
    XP (1 XP for 10 credits)\\

    \section{Mechs}

    \subsection{Sizes}
    [human is roughly 0.75]\par
    \begin{tabular}{r|l}
        Sizeclass &Mechclass \\
          0 &Human\\
        1-4 &Exo\\
        5-9 &Tiny\\
        6-7 &Very Light\\
        8-9 &Light\\
        10-11 &Medium\\
        12-15 &Heavy\\
        16-20 &Very Heavy\\
        21+ &Beyond\\
    \end{tabular}\newline
    Mechs have up to (SizeClass+(SizeClass+1))/2 Modules. Each modules weighs about 1 ton, Modules are listed below. \par
    A Mech has an effective Tech Level of the Tech at the 80\% point (of modules ordered by Tech Level).\newline
    Contamination Damage applies to the highest Tech modules first. Each Module can be damaged individually.\newline
    [rework in progress]\newline
    \newline

    \subsection{Systems}
    A Mech needs a movement system, a seal and energy and heat systems and should probably have weapons and Supportsystems\newline
    Armor, Shields and Movement Systems cant function together, You can switch between Movement Systems and designate the
    Order of Layers of Defense (damage taken by one armor, damages all armors though.)
    threshholds: percentage of movement system on mech for movement speeds. Cargo holds count as 8\% lighter per
    free space\newline

    Most Values given in the format A/B denote the passive value A / second and the active Value B/ second, \\
    for Fuel Consumption is given in Cargo per day / Cargo per minute.
    For Speeds are in km/h.

    \subsubsection{Costs}
    Systems(not all of these are in the game right now)\newline
    \begin{tabular}{c|c|l}
        Tech    & Credits Cost    & Examples\\
        B    &    4        &    \makecell*[{{p{12cm}}}]{Water Destillery, Rail based movement system, simple wheels,
        Manned gun, Ramshield, Floatation,   Metal Armorplating , Extra Cargo (10), steam engine, passive cooling}\\&&\\
        L    &    5        &    \makecell*[{{p{12cm}}}]{Lowtech Detox-Decon Equip(LDDE; +1), suspended wheels, tracks,
        bipedal, Dynamo , Autoturret, Jumpjets, Mech sized Sword, water cooling circle, basicHeatsink }\\&&\\
        M    &    6        &    \makecell*[{{p{12cm}}}]{Shields, flexible/balanced bipedal, Boostjets,
        Deployable Solar Panel, Sensorarray,  MDDE (+2), Base AI system, Mech sized Weaponry (Advanced
        (Vibro/electro/Monofilament) Sword), Rocketlauncher, Water venting system, midtech Heatsink}\\&&\\
        H    &    7        &    \makecell*[{{p{12cm}}}]{BCI, Advanced AI, WeaponLaser, Sustained Flight,  Advanced
        Shields, Nano Repair Cloud, Automedic, OVERDRIVE mode, Hightech Heatsink}\\&&\\
        E    &    8        &    \makecell*[{{p{12cm}}}]{Quantum Lookahead Sensors, Blink Teleporter, Timerift Shields
        (Delays Damage 1d10 rounds), EnergySword}
    \end{tabular}\\\\[12mm]

    \subsection{Movement Systems}
    \begin{tabular}{l|lcccl}
        Type    &Modes &Energy &Heat &Speed &Extra\\
        \hline
        Basetech\\
        railbased movement system & Rails &0.01/0.02&0/0&50/100& confined to rails\\
        &&&&&Accelleration in 15 rounds\\
        simple wheels           & Roads &0.1/0.3 &0.1/0.2& 10/40 & requires sufficiently flat terrain \\
        & Offroad&0.5/1&0.3/0.5& 5/10 & might topple\\
        floatation system         & Water & 0/5  &  0/0  & 0/1   & allows movement on water\\
        &       &     &       &       & Counts double For speed percentage\\
        \hline
        Lowtech\\
        suspended wheels          & Roads &0.05/0.5 &0.15/0.2& 30/70 & requires sufficiently flat terrain \\
        & Offroad&0.2/.8&0.5/0.8& 10/30 & might topple\\
        tracks                    & Offroad&0.5/1&0.5/1.2& 30/120 &Counts double For speed percentage\\
        & Harsh Terrain&1/2&1/2& 10/50 &\\
        bipedal                   & Ground &0.1/0.8&0.1/0.5& 3/30 & Full Dodge\\
        &&&&&Min Tracking: Speed\\
        &&&&&2 Arms with rough Gripper\\
        jumpjets                  & Air &0/10&0/10&0/50& Counts triple for speed percentage\\
        \hline
        Midtech\\
        flexible bipedal          & Ground &0.3/1.2&0.1/0.5 & 5/35 & Maneuverable like a large Human\\
        &&&&&Full Dodge\\
        &&&&&MinTracking: Speed\\
        &&&&&2 Arms with Robothands\\
        boostjets                 & Air &0/15 &0/20&0/150& acceleration in any direction\\
        &&&&&Counts Triple for speed percentage\\
        \hline Hightech\\
        Spiderwalker              & Surfaces &0.8/2 &1/3& 5/50 &moves on any surface\\
        &&&&& ...many legs
    \end{tabular}\\
    \subsubsection{Requirements}
    \begin{tabular}{c|c|c|c}
        speed       &Level  &needed\%& speed\% \\\hline
        lumbering   &1      &5\%     &33\%\\
        slow        &2      &15\%    &75\%\\
        normal      &3      &25\%    &100\%\\
        fast        &4      &35\%    &150\%\\
        rapid       &5      &45\%    &200\%\\
    \end{tabular}\\\newline\\
    Accelleration is the modified maximum speed divided by 5 per round unless otherwise stated
    \subsection{Seals}
    \begin{tabular}{l|r|r}
        Tech & Seal Level & Cost(round up)\\\hline
        Base &  6 &  3+0.1*Module\\
        Low &   13&  7+0.2*Module\\
        Mid &   21&  12+0.3*Module\\
        High &  30&  18+0.4*Module\\
        Experimental & 50&30+0.8*Module\\
    \end{tabular}\\
    \subsection{Heatsystems}
    \begin{tabular}{r|lllll}
        Type & Storage & Dissipation & Signature &Costs &Extra\\
        \hline Basetech\\
        Small Heatsink & 15 & 0.2 &Storage\\
        \hline Lowtech\\
        Radiator Vent & 3 & 1/6& Vented\(\cdot\)2&0.2/0.8\\
        Large Heatsink & 20 & 0.2[15]0.5 &Storage\\
        \hline Midtech\\
        Optimized heatsink & 25 & 0.4[15]0.8[25]1 &Storage\\
        Coolant Dump & 30 & 1/15 & Storage/30 & 0.3/1
        & Requires Decoy Rating of 3\\
        &&&&&uses 0.1 Water from Cargo and deploys \\
        &&&&&5m Thermal Wall of Strength 30 while active\\
        \hline Hightech\\
        fractal heatsink & 30& 0.5[15]1[30]1.5& Storage\\
        OVERDRIVE & 80 & 0.5 & Storage & Filling up &
        when at heatcap, enter Overdrive Mode\\
        &&&&&able to act (including movement) at double \\
        &&&&&speed while spending Heat instead of gaining it\\
        &&&&&When All heat is spent. Mech shuts down for \\
        &&&&&2d10(added) rounds and OVERDRIVE is \\
        &&&&&damaged (requires 10 min, Check[8] to repair)\\
        &&&&&(requires Level 4 Specialty Gadgets)\\
    \end{tabular}\\

    \subsection{Energysystems}
    \begin{tabular}{l|cccll}
        Type & Energy & Heat & Storage & Consumption & Special\\
        \hline Basetech \\
        Burner & -0.01/-0.5 & 0.1/5 & 20 H & 0.1/0.01 & Fuel:Coal\\
        Steam Engine & 2/5 & -1/-2.5 & 5 Energy & Heat & 10\% Efficient with Heat under 50\%\\
        FlyWheel & 0/1 & 0/X & 10 E & 0.01 of stored & retrieves half, generates \\
        &&&&&Heat 2:1 while retreiving\\
        Crank & 0/0.001&0/0&&Manual Labor&Size 0.01\\
        \hline Lowtech \\
        Combustion Motor& 0.5/3 & 0.5/3& & 0.01/0.005 & Fuel:CombustionFuel\\
        \hline Midtech \\
        PEM & 0.5/3.5 & 0.1/0.5 & & 0.05/0.02 & Fuel: HFC\\
        Solar Panel & 0/0.03 & 0/0 & 50 E & Sunlight & Contamination might lower yield\\
        &&&&&Deployment takes 1 Energy or\\
        &&&&&5 Minutes outside Labor\\
        &&&&&1 Heat per Energy Retrieved\\
        \hline Hightech \\
        Reactor & 1.2/2 & 0.8/1.5 & 100 E & 0.001/0.001 & Fuel:Fuelrods\\
        &&&&&0.5 Heat per Energy Retrieved\\
        Capacitor & & X & 500 E & & 0.1 Heat per Energy Retrieved \\
    \end{tabular}
    \vspace{1cm}

    a 10L-HydrogenFuelCell(HFC-10) Cylinder 20cm diameter, 38 cm height =11.94L(Midtech),
    used to power up basic systems (like hydrogen gas pumps for the PEM Stacks)

    \subsection{Shieldsystems}
    ShieldModules can be dedicated to specific Tasks, usually
    Coverage (C) and Reboot(R), the total amount of Modules is referred to as M, while
    X relates to Special, see below the Table\newline
    \begin{tabular}{c|cccccl}
        Type & Level & Cost & Overwhelm & Coverage & Reboot & Coldboot \\
        \hline Basetech\\
        Applique-Armor & 3 & 0/0 & destroy F& 5+15\(\cdot\)C & -  & 5 min + \\
        &&&block&&& Check[Engineer](5) \\
        \hline Lowtech\\
        Deflector & X & 1E/5E+3H & - & radius 2\(\cdot\)C m & 10s & instant \\
        Basic Shield & 1 & 0.5E/0.2E & \makecell{5H, dampen, \\disable}&12+C\(\cdot\)8 & C-R + 5E & 5r \\
        \hline Midtech\\
        Shield & 2 & 1/0.5(2H) & \makecell{7H, dampen,\\disable} & 10+C\(\cdot\)13 & 12/R (round up) & 10 E \\
        \hline Hightech\\
        Advanced Shield & 4 & 1/2(3H) & \makecell{15H, block,\\disable}& 15+C\(\cdot\)10 & 8-R + 10E & 5r \\
    \end{tabular}\newline\newline\newline
    Level: see 3d10 Table in the beginning of the Book\\
    Cost: for Charging/Active states, per round\\
    Overwhelm: Heat that might be released plus \\
    \tab destroy X destroys X modules\\
    \tab F means the difference by which the Layer of Defense Failed\\
    \tab block means pass through no damage to the next Layer of Defense\\
    \tab dampen means pass through F damage\\
    \tab disable means that the system is disabled until it is booted again\\
    \newline
    Strain: Heat Costs in Parenthesis are generated everytime the shield successfully blocks damage. D is the Incoming damage.
    \pagebreak[2]
    \subsection{Armor}
    \begin{tabular}{c|cccll}
        Type & Level & HP & Coverage & Damage & Special\\
        \hline BaseTech&&&&&\\
        Extended Cargo & 1 & \makecell{\(\sqrt{M}\)\\ rounded down}& 14\(\cdot\)M & destroy 1 & \makecell[{{p{6cm}}}]{7 Cargo Spaces (Cargo is destroyed with the modules)}\\
        Metal Plating & 4 & 5 & 5+10M & destroy F & \makecell[{{p{6cm}}}]{counts twice towards movement system percentage} \\
        \hline Lowtech &&&&&\\
        Composite & 4 & \makecell[c]{\(2\cdot\sqrt{M}\)\\ rounded}& \(12\cdot M\) & destroy 1&\\
        \hline Midtech &&&&&\\
        Active & 1/4 & 5 & 12+10\(\cdot\)M & short out 1 & \makecell[{{p{6cm}}}]{ draws 10 Energy when hit \\
        1h Check[Electronics] \\(>=8 to fix; <=2 to destroy)}\\&\\
        Speed & 2 & 3 & 20+7M & brick 50\% & \makecell[{{p{6cm}}}]{1E/50km/h; \\Vent 1H/ 50 km/h \\
        (increase signature by vented Amount) \\30m 0.1MTS Check[Engineer]\\(>=9 to fix; <=5 to destroy)}\\
        \hline Hightech &&&&&\\
        Advanced & 5 & X & 10+15\(\cdot\)M & \makecell[l]{shorts out \\ 1 Energy System}&\makecell[{{p{6cm}}}]{
        1h Check[Electronics] \\(>=8 to fix; <=2 to destroy)}\\
    \end{tabular}\\\newline\newline
    \subsection{Weapons}
    Weapon modules can also be dedicated\newline
    Melee weapons rely on the movement System, so their costs are in meters that are used to attack rather than move\newline
    \begin{tabular}{c|cccclll}
        Type & Level & Size &\makecell{Size\\Class} & \makecell{Damage\\Type} & Costs & Falloff &Check\\
        \hline BaseTech&&&&&\\
        Metal Sword & 2 & M & 2*S & P S &  30 m & 2m*S & Piloting \\
        Manned Turret & X & 1 & X & X & \makecell[l]{manual \\labor +X} &  X & \makecell[{c}{p{3cm}}]{X}\\
        \hline Lowtech &&&&&\\
        Heavy Machinegun & 4 & 1 & 3 & P R & 0.5H 0.005A & 50/100/200/500/1000 & Projectile.Direct\\
        Light Artillery & 3 & 4 & 15 & P A & 5E 10H 0.2A & 1k/3k/5k/7k/10k & Projectile.Indirect \\
        120mm Smoothbore & 5 & 4 & 8 & P S & 5H 0.05A & 500/1k/2k/3k/4k & Projectile.Direct\\
        \hline Midtech &&&&&\\
        Autocannon & \makecell[c]{~2/\\4} & 3 & 7 & \makecell[c]{P/\\P R} &\makecell[l]{0E 2H 0.01A /\\1E 5H 0.15A }& per 400m & Projectile.Direct\\
        Basic Pulse Laser & 2 & 2 & 9 & E S & 5E 8 H & per 200 & Energy.Pulse\\
        Precision Cannon & 2 & 3 & 13 & P S & 5E 10H 0.1A & per 1k & Projectile.Direct\\
        Rocket Launcher & 4 & 2 & 15 & P S & 5H 0.12A &per 300m & Rocket.Dumbfire\\
        \hline Hightech &&&&&\\
        Rocket Platform & 3 & 3 & 16 & P S A & 5H 0.2A & - & Rocket.Guided \\
        Railgun & 2 &5& 14 & P S & 15E 5H 0.01 A& 100/1k/3k/8K/20k & Projectile.Direct\\
        Advanced Pulse Laser & 0 & 3 & 11 & E S/R & 7E 8H  &per 400 & Energy.Pulse \\
        Ramping Beam Laser & X & 2X & 3 & E R        & XE 2XH & per 5k & Energy.Beam \\
    \end{tabular}\newline\newline\newline
    Specials:
    Swords: Pierce Shields that are not modulated to their damage type\\
    Manned Turret: X Depends on the mounted gun and the skill of the gunner\\
    Light Artillery: Attacks take 1s per 300m distance, rounded up, minimum range 100m\\
    120mm Smoothbore: Can only fire every second round, requires Indirect for targets further away than 2k\\
    Autocannon: for Burst (alternative values) mode Mech has to stand\\
    Basic Pulse Laser: only sizeclass falls off\\
    Precision Cannon: Allows Sniping \\
    Rocket Launcher: Ignores Shields \\
    Rocket Platform: Ignores Shields, Will hit if Lock is sustained (Roll strengthens Lock)\\
    Railgun: requires Indirect for targets further away than 2k, allows sniping\\
    Advanced Pulse Laser: only sizeclass falls off\\
    Ramping Beam Laser: X goes up when shooting, goes down when not shooting, X is capped at M, allows sniping,
            only sizeclass falls off\\


    \subsection{Misc Modules}
    If a Module is smaller than a Module slot its size is less than 1
    \newline
    \subsection{Basetech}
    Water Distillery \\
    Energy Cost: 2\\
    Heat: 10\\
    Size: 0.5\\
    Turns 10L of Dirty Water into 10L of Contaminated Water per hour\\
    Requires Detox Rating of 1\\
    \newline
    Cargo compartment\\
    Cargo Space: 10 \\
    \newline
    \subsection{Lowtech}
    Basic Food Processor\\
    Energy Cost per operation: 1800 (3e/s)\\
    Heat: 5/s \\
    Size:0.5\\
    Detoxes 1kg of Food in 10 minutes \\
    Requires Detox Rating of 2\\
    \newline
    Basic Air Filter\\
    Energy Cost per operation: 2400 (4/s)\\
    Heat: 2\\
    Size:0.5\\
    Decontaminates and pressurizes 5000 L of air in  10 minutes or double without pressurizing. \\
    Requires Decon 1\\
    \newline
    Basic Decon Equipment \\
    Energy Cost per operation: 18k (5/s)\\
    Alacast Cost per operation: 10g\\
    Heat: 10 \\
    Size: 0.5\\
    Allows to turn Contaminated Objects into uncontaminated objects at the rate of 10kg/h, if suitable\\
    Required Decon 2\\
    \newline
    Optical Sensors\\
    Energy: 1\\
    Size: 0.25 \\
    Rating: 100\\
    Provides Targetting Lock is obtained\\
    Visual Lock: Distance/Rating <= Target Size (+Camouflage and visual impairments)\\
    \newline
    Thermal Sensors\\
    Energy: 1\\
    Size 0.25\\
    Rating 100\\
    Thermal Lock: Distance/Rating <= Target Thermal Signature\\
    \newline
    Basic Computer System\\
    Size: 0.5\\
    Energy: 0.1\\
    Module: Processor or Memory\\
    \newline
    \subsection{Midtech}
    ComputerSystem:
    Size: 0.1
    Energy: 0.1
    Module: Processor or Memory\\
    \newline
    Nondeterministic Computation Core:\\
    Size 0.5\\
    Energy: 0.5\\
    Module: Processor\\
    Requires Black Biotech 3\\
    \newline
    Extended Decon Equipment\\
    Energy Cost per Operation: 36k (10/s)\\
    Alacast Cost per Operation: 5g\\
    Size: 0.75
    Allows to turn Contaminated Objects into uncontaminated Objects at the rate of 100kg/h if suitable\\
    If used on Humans, Roll Red Biotech, on 9 or more, removes one Charactertaint.\\
    Always Inflicts Wound of Level 11-RollResult\\
    Requires Decon 3\\
    \newline
    Extended Detox Equipment:\\
    Energy Cost per Operation: 36k (10/s)\\
    Size 0.75\\
    Allows Detoxing and Preparing of up to 1t/h\\
    If used on Humans, Roll Red Biotech, on 6 or more, remove all Infections and appropriate Toxins.\\
    Always Inflicts Wound of Level 8-RollResult\\
    Requires Detox 3\\
    \newline
    Automedic:
    Energy Cost: 6k(variable - 10/s for 10 min)\\
    Size: 0.75\\
    Supplies tools of Medic/ supplies good operating conditions for Medic / reduces the use of Medicine by half / allows stasis\\
    Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
    double Advantage or autonomously attempts the procedure at Level 3 mod -1.\\
    If not, Instead supplies one Advantage.\\
    Software may supply the Red Biotech roll even autonomously.\\
    Stasis is automatic and slows down the daily/hourly tickrate (including Healing and Contamination) by a factor of 10
    (additive) for every energy point per second. This is a medical coma, not timedilation.

    \subsection{Hightech}
    Advanced Detox-Decon Equipment \\
    Size: 1\\
    Energy Cost per Operation 72k (variable 20/s for 1 h)\\
    Alacast Usage per Operation if Detainting: 1g/t of raw material, 10g/human\\
    Detoxes and Detaints up to 5t of material, including air and water.\\
    Living Entities suffer no harm, and on a 4 or more on a Red Biotech Roll lose one Taint level.
    Furthermore all Infections and Appropriate Toxins are removed.\\
    Requires Detox 4 and Decon 4\\
    \newline
    Advanced AutoMedic\\
    Energy Cost: 3k (variable - 5/s for 10 min)\\
    size: 1\\
    Allows Medic Rolls/ supplies very good operating conditions for Medic Rolls/ reduces the use of Medicine by 90\%/allows Ressurection\\
    To Treat a wound:\\
    Roll Red Biotech, if the roll surpasses the wound, supplies an operating character with a temporary Medic skill and
    triple Advantage or autonomously attempts the procedure at Level 4 mod -1.\\
    If not, Instead supplies one Advantage or autonomously attempts the procedure at Level 2.\\
    Software may supply the Red Biotech roll even autonomously.\\
    To Ressurect:\\
    requires 1g of EOL per total spent points on a character (or 20* the average level of an NPC)
    Roll Black Biotech, every 15\% missing from the corpse or order of magnitude in days that has passed since the time of death
    lowers the final score by 1. If the roll succeeds, place 5 wounds of severity 15-result on that character, they lose
    one level from the highest Ability and one from the highest Skill and are alive again. If the roll does not succeed,
    5\% of the total corpse and the dosage of EOL is lost.
    \newline






\end{document}
