\begin{tabular}{|r|l|}
    \hline
    Storage & Article\\\hline
    10g & Elixir of Life (EOL)\\\hline
    100g & Alacast\\\hline
    500g & Experimental Tech Scrap (ETS)\\\hline
    1kg & High Tech Scrap (HTS)\\\hline
    1.5kg & Advanced Gene Therapy Medicine (AGT)\\\hline
    5kg & Medium Tech Scrap (MTS)\\\hline
    10kg & Potent Medicine\\\hline
    50kg & Low Tech Scrap (LTS)\\\hline
    50kg & Seeking Rockets\\\hline
    100kg & Processed Medicine\\\hline
    100kg & Basic Rockets\\\hline
    100kg & Artillery\\\hline
    200kg & Basic Medicine\\\hline
    500kg & Improvised/Herbal Medicine\\hline
    500kg & Base Tech Scrap (BTS)\\\hline
    500kg & Basic Ammunition\\\hline
    1000L & drinking Water (500days of drinking)\\\hline
    500L/35kg & Liquid Hydrogen\\\hline
    1t & Coal\\\hline
    350L & LiquidCombustionFuel\\\hline
    100kg & High Energy Rations (0.4kg/(day\(\cdot\)person))\\\hline
    1t & Normal Food (2.5 kg / (day\(\cdot\)person))\\\hline
    1 & Medium Quality Blueprint\\\hline
\end{tabular}\par
Open for more Suggestions\vspace{1.5cm}
Example:\par
Character A wants to get rid of 5 tonnes of Base Tech Scrap in favor of more easily transportable Alacast in a local
Dome.\par
Since the Gamemaster is lazy there are no storyelements influencing the prices, so they are rolled.
First, the value of
the BTS is determined to be (Roll: 6, 4) \(((-1)^{6}\cdot4\cdot5) \% = +20\%\).
Then the value of Alacast is determined
to be (Roll: 10, 3)\(((-1)^{10}\cdot3\cdot5) \% = +15\%\).
The result is that the rate between BTS and Alacast is
\( 500\cdot1.15/100\cdot1.2 = 4.79\) \\ Which means character As scrap is worth
\(5000 kg\cdot / 4.79 = 1043 g \) of Alacast.
He barters (in which he has Proficiency) with a local merchant and manages to
negotiate terms in which the merchant retains (Roll: 4, 9 \(\Rightarrow\) 9) \(5\cdot(11-9)\% = 10\%\) of the Traded
value.
He decides to trade and gets 938 grams of Alacast.\vspace{1.5cm}
\pagebreak

\chapter{Combat}\label{ch:combat}
\subsection{Life}\label{subsec:life}
Every entity has a pool of Hitpoints, which describes how far away that entity is from its failure point.
In the case of a Mech, Mount or Human, that would mean being unable to fight or act in an effective manner.
Living
entities start dying when they have twice as many wounds as hitpoints.
How fast something dies is decided by the
Gamemaster.\par
If an entity gets damaged, the result of the damage roll (or the number set by the Gamemaster) is compared the results
of rolls made by the outermost layer of defense.
If the result of the damage is higher, it, depending on the
layer of defense, gets blocked, passes through or overwhelms the layer.
If damage passes all layers of defense,
it causes damage of a severity of the remaining result.
Biological Entities for a Biological Entity this is called a wound.
\subsection{Rounds}
Combat is done in rounds.
Each round is 5 seconds long.
Every character present acts in turn (determined
by circumstances or a Stealth, Perception, Willpower or other situational check) and can usually move and do an action
(an attack or action that can be done in the remaining time).
\subsection{Combat against Groups}
The Group is treated as a single Enemy with its pool of Hitpoints being its members.
It gets offensive/defensive Levels and modifiers assigned by the Gamemaster.\\
The fighting character decides (if possible, depending on gear and situation) to fight offensively, defensively
or passively and rolls the respective combat stat, then the differences between each of the rolled dice of the combat
roll and the groups performance value is calculated.\par
\begin{enumerate}[label= - ]
    \item Offensive style: For every step of severity in the damage dealt (with an appropriate weapon),
    a Group member is rendered unable to
    fight.
    On Offensive rolls, the group gets a sizebonus correlating to their size and an advantage.
    \item Defensive style: Dealing damage results in a group member being rendered unable to fight.
\end{enumerate}
\subsection{Detailed combat}
The attacking character makes their to hit check (dexterity for example).
The defending character Checks for the
corresponding defense (agility for example).
If the attacker wins, they hit, on a draw the
attack grazes.
On a hit, check for damage by rolling the damage level of the weapon, subtract the result of the
armor roll and add difference in sizeclasses between weapon and target.
If all levels of Defense are breached, the remaining result of the roll is the severity of the inflicted damage.\par
When sniping, The damage is not inflicted in general, but on a part of the target with a maximum depth equal to
the severity of the damage.
For the rest see sniping.