These entries in the table below are usually equivalent, local supply and demand may vary them greatly.
Rolling for price variance might be done if there is no in-world reason why certain things might be more or
less expensive.
If that is the case the prices vary by \(((-1)^{1d10}\cdot1d10\cdot5) \%\).
Additionally everyone a character trades with has self interest and will keep some of
the tradevalue.\par
\begin{tabular}{cccccccc}
threshhold&0&5&8&11&14&17&20\\
kept tradevalue&50&33&20&10&5&2&0
\end{tabular}\\
Goods, at 100\% value each line is equivalent to one another and equivalent to 4 character creation points \par
\section{Tradegoods}\label{sec:tradegoods}
\begin{tabular}{|r|l|}
    \hline
    Storage & Article\\\hline
    10g & Elixir of Life (EOL)\\\hline
    100g & Alacast\\\hline
    500g & Experimental Tech Parts (ETP)\\\hline
    1kg & High Tech parts (HTP)\\\hline
    1.5kg & Advanced Gene Therapy Medicine (AGT)\\\hline
    5kg & Medium Tech parts (MTP)\\\hline
    10kg & Potent Medicine\\\hline
    50kg & Low Tech parts (LTP)\\\hline
    50kg & Seeking Rockets\\\hline
    100kg & Processed Medicine\\\hline
    100kg & Basic Rockets\\\hline
    100kg & Artillery\\\hline
    200kg & Basic Medicine\\\hline
    500kg & Improvised/Herbal Medicine\\\hline
    500kg & Base Tech parts (BTP)\\\hline
    500kg & Basic Ammunition\\\hline
    1000L & drinking Water (500days of drinking)\\\hline
    500L/35kg & Liquid Hydrogen\\\hline
    1t & Coal\\\hline
    350L & LiquidCombustionFuel\\\hline
    100kg & High Energy Rations (0.4kg/(day\(\cdot\)person))\\\hline
    1t & Normal Food (2.5 kg / (day\(\cdot\)person))\\\hline
    1 & Medium Quality Blueprint\\\hline
\end{tabular}\par
Open for more Suggestions\vspace{1.5cm}
Example:\par
Character A wants to get rid of 5 tonnes of Base Tech Scrap in favor of more easily transportable Alacast in a local
Dome.\par
If there are no storyelements influencing the prices, they are rolled.
First, the value of the BTP is determined to be (Roll: 6, 4) \(((-1)^{6}\cdot4\cdot5) \% = +20\%\).
Then the value of Alacast is determined
to be (Roll: 10, 3)\(((-1)^{10}\cdot3\cdot5) \% = +15\%\).
The result is that the rate between BTP and Alacast is
\( 500\cdot1.15/100\cdot1.2 = 4.79\) \\ Which means character As scrap is worth
\(5000 kg\cdot / 4.79 = 1043 g \) of Alacast.
He barters (with Resolve and Trade for 3, 2) with a local merchant and manages to
negotiate terms in which the merchant retains (Roll: 2, 4, 5, 8, 9 \(\Rightarrow 9 \Rightarrow 10\%\) of the Traded
value.
He decides to trade and gets 938 grams of Alacast.\vspace{1.5cm}
\pagebreak
